---
title: "Analysis"
output: html_document
---


```{r, echo = FALSE, message = FALSE}
source(here::here("scripts/Setup.R"))
```


### Work environment 

We decide to do a cluster analysis to see if there is some prevalence of certain region compared to others, and also wanted to study our problem through another perspective, that of the countries. Indeed, we could notice on the first plots, some countries adopt more extreme behaviors (position separated from the others) and it is often the same across the different variables.  A good way to analyze this is to group our countries using clusters. The goal is to see if the work environment has more impact in some countries
than in others on the mental health of its population. This is also where we will use our table of averages that we made for each of the variables.


# ATTENTION MARCHE PAS SI NA DONC JE LES ENLEVE POUR L'INSTANT
```{r, echo = FALSE, message = FALSE}
tab_mean_na <- na.omit(tab_mean)
```
# Table ? : Cluster analysis for each of our explanatory variables
```{r}
# Income Inequality
data_t0 <- tab_mean_na[-1]
data_t0 <- data_t0[,c(2,1)]
mean_data <- apply(data_t0, 2, mean)
std <- apply(data_t0,2,sd)
data_t0_std <- scale(data_t0, mean_data, std)
row.names(data_t0_std) <- tab_mean_na[,1]
distance <- dist(data_t0_std)
hc <- hclust(distance)
avclust <- hclust(distance, method = "average")
km.res <- kmeans(data_t0_std, 5)
C0 <- fviz_cluster(km.res, data=data_t0_std, repel = TRUE) 

# Wages
data_t1 <- tab_mean_na[-1]
data_t1 <- data_t1[,c(3,1)]
mean_data <- apply(data_t1, 2, mean)
std <- apply(data_t1,2,sd)
data_t1_std <- scale(data_t1, mean_data, std)
row.names(data_t1_std) <- tab_mean_na[,1]
distance <- dist(data_t1_std)
hc <- hclust(distance)
avclust <- hclust(distance, method = "average")
km.res <- kmeans(data_t1_std, 5)
C1 <- fviz_cluster(km.res, data=data_t1_std, repel = TRUE)

# Unemployment
data_t2 <- tab_mean_na[-1]
data_t2 <- data_t2[,c(4,1)]
mean_data <- apply(data_t2, 2, mean)
std <- apply(data_t2,2,sd)
data_t2_std <- scale(data_t2, mean_data, std)
row.names(data_t2_std) <- tab_mean_na[,1]
distance <- dist(data_t2_std)
hc <- hclust(distance)
avclust <- hclust(distance, method = "average")
km.res <- kmeans(data_t2_std, 5)
C2 <- fviz_cluster(km.res, data=data_t2_std, repel = TRUE)

# Working Age
data_t3 <- tab_mean_na[-1]
data_t3 <- data_t3[,c(5,1)]
mean_data <- apply(data_t3, 2, mean)
std <- apply(data_t3,2,sd)
data_t3_std <- scale(data_t3, mean_data, std)
row.names(data_t3_std) <- tab_mean_na[,1]
distance <- dist(data_t3_std)
hc <- hclust(distance)
avclust <- hclust(distance, method = "average")
km.res <- kmeans(data_t3_std, 5)
C3 <- fviz_cluster(km.res, data=data_t3_std, repel = TRUE)

# GDP
data_t5 <- tab_mean_na[-1]
data_t5 <- data_t5[,c(7,1)]
mean_data <- apply(data_t5, 2, mean)
std <- apply(data_t5,2,sd)
data_t5_std <- scale(data_t5, mean_data, std)
row.names(data_t5_std) <- tab_mean_na[,1]
distance <- dist(data_t5_std)
hc <- hclust(distance)
avclust <- hclust(distance, method = "average")
km.res <- kmeans(data_t5_std, 5)
C4 <- fviz_cluster(km.res, data=data_t5_std, repel = TRUE)

# Put all the graphs together
plot_grid(C0, C1, C2, C3, C4, labels=c("A","B","C","D","E","F"), ncol=3, nrow=2)
```

This table ? shows us that, regardless of the work environment variable, we always have a clear demarcation. Indeed, it is always the same countries in the same places. We can therefore conclude that each region has its own specificities related to the work environment that impact the rate of mental health disorders. 

It would therefore be interesting to see how these behave according to the regions. 

```{r, echo = FALSE, message = FALSE}
mod2 <- lm(tab$Mental_Health ~ tab$Region + tab$TIME)
summary(mod2)
```




#### COVID 

# Regression Antidepressant Consumption / Covid Cases, Deaths + correlation


```{r, echo = FALSE, message = FALSE}

cor(tab_R2.1$Antidepressant_Consumption, tab_R2.1$Deaths)
cor(tab_R2.1$Antidepressant_Consumption, tab_R2.1$Cases)
```

We obtain a correlation of "0,0049" between antidepressant consumption and the number of deaths due to covid, and a correlation of "0,0453" between antidepressant consumption and Covid cases.  
Moreover, for the regression between consumption and the number of covid cases, we obtain an R^2 = 0.024. This means that the "cases" variable explains 2.4% of the variance of the model, which is not a good result. 

Unfortunately, we can see that there is no correlation between these variables, either with the number of cases or the number of deaths. 
We can give several explanations to this surprising observation.

The first one is the lack of data. Indeed, we were able to study the evolution of antidepressant consumption in only 8 countries. Perhaps with more countries, we would have seen a more significant difference. 

The second and the most likely, is that we can see that the number of cases (and deaths) related to covid are huge numbers, going from 0 to several millions (to thousands). However, compared to these numbers, the value of antidepressants consumption is increasing well as we can see in the graph below but not as much as the number of cases. The ratio is not the same. 

We will now calculate the value of the increase in consumption, by years and see if we can observe a difference between years or not, and compare it to the value of the consumption in 2020.  

```{r, echo = FALSE, message = FALSE}
#Tableau antidepresseurs, croissance chaque année
tab_R2.1G <- ddply(Antidepressant_consumption2, .(LOCATION),
                                  function (d) {
                                    d$Growth <- c(NA, tail(d$Antidepressant_Consumption, -1) - head(d$Antidepressant_Consumption, -1))
                                    d
                                  }
)

#Tableau croissance jusqu'en 2019
tab_R2.1.2019 <- tab_R2.1G %>%
  group_by(LOCATION,Growth) %>%
  filter(TIME< 2020)

#Moyenne croissance jusqu'en 2019
tab_R2.1mean <-aggregate(tab_R2.1.2019[,4], list(tab_R2.1.2019$LOCATION), mean, na.rm=T)
tab_R2.1mean <-rename(tab_R2.1mean, "LOCATION" = "Group.1")

#Tableau conso 2020 et croissance entre 2019 et 2020
tab_R2.1.G2020 <- tab_R2.1G %>%
  group_by(LOCATION,Growth) %>%
  filter(TIME == 2020)
  
#Tableau croissance entre 2019 et 2020
tab_R2.1.G2020 <-tab_R2.1.G2020[-3]

#Tableau moyenne croissance jusqu'en 2019 et croissance 2019/2020
comparaison <- merge(tab_R2.1mean,tab_R2.1.G2020, by = c("LOCATION"))
comparaison <- rename(comparaison, c("Growth_mean"="Growth.x","Growth2020"="Growth.y"))
comparaison <- comparaison[-3]

#Tableau moyenne conso jusqu'en 2019 
consumptionMean <- aggregate(tab_R2.1.2019[,3], list(tab_R2.1.2019$LOCATION), mean)
consumptionMean <-rename(consumptionMean, "LOCATION" = "Group.1")

#On ajoute conso moyenne a comparaison
comparaison <- merge(comparaison,consumptionMean, by = c("LOCATION"))
comparaison <- rename(comparaison,"Consumption_mean"="Antidepressant_Consumption")

#Tableau Conso 2020
consumption2020 <- tab_R2.1 %>%
  group_by(LOCATION,Antidepressant_Consumption) %>%
  filter(TIME == 2020)
consumption2020 <- consumption2020[-4]

#On ajoute conso 2020 a comparaison 
comparaison <- merge(comparaison,consumption2020, by = c("LOCATION"))
comparaison <- comparaison[-5]
comparaison <- rename(comparaison,"Consumption2020"="Antidepressant_Consumption")

kable(comparaison)
```

When we calculate the average consumption from 2000 to 2019 and compare it to the consumption in 2020 we notice that the latter is for all countries higher than the average of the previous years. 
Then, when we compare the average growth in consumption per year, to the growth between 2019 and 2020, we see that the latter is higher than the average for 5 of the 8 countries analyzed (Portugal, Italy, Iceland, Hungary and Greece). 

This shows that the consumption of antidepressants has increased in 2020, which could be well explained by the covid crisis. 

# Countries with the highest and lowest deaths covid / Depression Rate 2021

```{r, echo = FALSE, message = FALSE}
covid <- Number_Covid19_cases_deaths %>%
  filter(LOCATION %in% List.of.Countries)

deaths.tophigh <- covid %>% arrange(desc(Deaths)) 
deaths.tophigh <- deaths.tophigh[1:13,] %>% select(LOCATION,Deaths)

deaths.toplow <- covid %>% arrange(Deaths) 
deaths.toplow <- deaths.toplow[1:13,] %>% select(LOCATION,Deaths)


kbl(
  tibble(
    'Top Countries' = deaths.tophigh$LOCATION,
    "TCDeaths " = deaths.tophigh$Deaths,
    'Low Countries' = deaths.toplow$LOCATION,
    "LDeaths" = deaths.toplow$Deaths
  ),
  caption = "**Table 1**: countries with the most and least deaths of covid in 2020 .",
  align = c("lclc")
) %>%
  kable_classic(full_width = T, html_font = "Cambria") %>%
  kable_styling(bootstrap_options = c('striped', 'hover', 'condensed'),table.envir = "table") %>%
  column_spec(c(1,3), width = "8cm")




List.top.deaths <- c("HUN","CZE","BRA","ROU","HRV","BEL","USA","ITA","POL","ESP","FRA","PRT","GRC")
List.low.deaths <- c("CHN","NZL","AUS","ISL","JPN","NOR","FIN","CAN","NLD","DEU","AUT","CHE","SWE")

tableau.top.deaths <-  Depression_Rate2021 [-3]%>%filter(LOCATION %in% List.top.deaths) 
mean.top.rate.deaths <- mean(tableau.top.deaths$Depression_Rate)

tableau.low.deaths <- Depression_Rate2021 [-3]%>% filter(LOCATION %in% List.low.deaths)
mean.low.rate.deaths <- mean(tableau.low.deaths$Depression_Rate)

plot3 <- ggplot(data=tableau.top.deaths)+
  geom_bar(aes(x = Depression_Rate, y= LOCATION),fill = '#0099CC',stat = "identity")+
  geom_text(aes(x = Depression_Rate, y = LOCATION, label = paste(round(Depression_Rate, digits = 2),"%")),
            hjust = 1.15,color='white')+
  ylab("top Covid Deaths")+
  xlab("") +
  xlim(c(0,6))


plot4 <- ggplot(data=tableau.low.deaths)+
  geom_bar(aes(x = Depression_Rate, y= LOCATION),fill = '#FF3399',stat = "identity")+
  geom_text(aes(x = Depression_Rate, y = LOCATION, label = paste(round(Depression_Rate, digits = 2),"%")),
            hjust = 1.15,color='white')+
  ylab("low Covid Deaths")+
  xlab("") +
  xlim(c(0,6))

ggarrange(plot3,plot4,nrow = 2,align = 'v') %>%
  annotate_figure(top = text_grob("Depression Rate For Countries with The Most and Least deaths of Covid in 2020", 
                                  size = 12),
                  bottom = text_grob("Depression Rate"))

kbl(tibble(
  'Top Covid deaths'=mean.top.rate.deaths,
  'Low Covid deaths'=mean.low.rate.deaths
),
caption = "**Average depression rate in countries with highest and lowest Covid-19 Deaths**",
align = c("cc")
) %>%
  kable_classic(full_width = T, html_font = "Cambria") %>%
  kable_styling(bootstrap_options = c('striped', 'hover', 'condensed'),table.envir = "table")
```



# Regression Antidepressant Consumption / Teleworking / Unemployment / TIME 


```{r, echo = FALSE, message = FALSE}
Reg2.2 <- lm(tab_R2.2$Consumption~tab_R2.2$Teleworking+tab_R2.2$Unemployment+tab_R2.2$TIME)
summary(Reg2.2)
```

With the *summary* function we can see a significant increase for one unit of  1.70310 * ValueAntidepressantConsumption for "Teleworking". This variable is significant with 2 stars wich is satisfying. However, "Unemployment" is not significant as it represents an increase for one unit of 0.04958 * ValueAntidepressantConsumption. 
However, R^2 is equal to 0,0867 which means that our model is explained by 8,7% of the variance, which is not very satisfying. This means that variables we don't know, have a more significant impact on antidepressant consumption in a country.

Given the results, and that the variable "unemployment" has not a significant impact on antidepressant consumption, we will remove this variable for the rest of our analysis. We will now now focus on teleworking and analize the link between this variable and antidepressant consumption with different graphs. 


# Countries with the most and least teleworkers on AVERAGE compared to antidepressant consumption 

```{r, echo = FALSE, message = FALSE}
tab_R2.2.2010 <- tab_R2.2 %>% filter(TIME > 2009)
#moyenne consommation antidepresseur par pays
mean.conso <- aggregate(tab_R2.2.2010[, 3], list(tab_R2.2.2010$LOCATION), mean)
mean.conso <- rename(mean.conso, c("LOCATION" = "Group.1","conso"="x"))

#moyenne teleworking par pays 
mean.teleworking <- aggregate(tab_R2.2.2010[, 4], list(tab_R2.2.2010$LOCATION), mean, na.rm=T)
mean.teleworking <- rename(mean.teleworking, c("LOCATION" = "Group.1","teleworking"="x"))


#pays avec le plus et le moins de telework 


teleworking.tophigh <- mean.teleworking %>% arrange(desc(teleworking)) 
teleworking.tophigh <- teleworking.tophigh[1:8,] %>% select(LOCATION,teleworking)

teleworking.toplow <- mean.teleworking %>% arrange(teleworking) 
teleworking.toplow <- teleworking.toplow[1:8,] %>% select(LOCATION,teleworking)


kbl(
  tibble(
    'Top Countries' = teleworking.tophigh$LOCATION,
    "TTeleworking " = teleworking.tophigh$teleworking,
    'Low Countries' = teleworking.toplow$LOCATION,
    "LTeleworking" = teleworking.toplow$teleworking
  ),
  caption = "**Table 2**: countries with the most and least teleworkers on average from 2010 to 2019",
  align = c("lclc")
) %>%
  kable_classic(full_width = T, html_font = "Cambria") %>%
  kable_styling(bootstrap_options = c('striped', 'hover', 'condensed'),table.envir = "table") %>%
  column_spec(c(1,3), width = "8cm")

#tableau antidepressant conso pour top tele

List.top.telework <- c("NLD","FIN","DNK","AUT","BEL","ISL","PRT","SWE")
List.low.telework <- c("HUN","GRC","CZE","DEU","ITA","ESP","NOR")

tableau.top.conso2 <-  mean.conso %>%filter(LOCATION %in% List.top.telework) %>% arrange(desc(conso)) 

mean.top.consumption <- mean(tableau.top.conso2$conso)

tableau.low.conso2 <- mean.conso %>% filter(LOCATION %in% List.low.telework)  %>% arrange(desc(conso))
mean.low.consumption <- mean(tableau.low.conso2$conso)

#tableau.low.conso2 %>% mutate(LOCATION= fct_reorder(LOCATION,conso)) #mettre ordre décroissant ? 

plot9 <-ggplot(data=tableau.top.conso2)+
  geom_bar(aes(x = conso, y= LOCATION),fill = '#0099CC',stat = "identity")+
  geom_text(aes(x = conso, y = LOCATION, label = paste(round(conso, digits = 2),"u")),
            hjust = 1.15,color='white')+
  ylab("top teleworking")+
  xlab("") +
  xlim(c(0,150))


#tableau antidepressant conso pour low tele

plot10 <-ggplot(data=tableau.low.conso2)+
  geom_bar(aes(x = conso, y= LOCATION),fill = '#FF3399',stat = "identity")+
  geom_text(aes(x = conso, y = LOCATION, label = paste(round(conso, digits = 2),"u")),
            hjust = 1.15,color='white')+
  ylab("low teleworking")+
  xlab("") +
  xlim(c(0,150))

ggarrange(plot9,plot10,nrow = 2,align = 'v') %>%
  annotate_figure(top = text_grob("Antidepressant consumption For Countries with The Most and Least teleworkers on average 2010/2019", 
                                  size = 12),
                  bottom = text_grob("Antidepressant consumption"))

kbl(tibble(
  'Top Teleworking countries'=mean.top.consumption,
  'Low Teleworking countries'=mean.low.consumption
),
caption = "**Average Antidepressant consumption in countries with highest and lowest teleworking**",
align = c("cc")
) %>%
  kable_classic(full_width = T, html_font = "Cambria") %>%
  kable_styling(bootstrap_options = c('striped', 'hover', 'condensed'),table.envir = "table")
```



# Antidepressant consumption in countries with the most teleworkers and least teleworkers in  2020

```{r, echo = FALSE, message = FALSE}
#consommation antidepresseur par pays
conso2020 <- tab_R2.2.2010 %>% filter(TIME == 2020) %>% rename("conso2020"="Antidepressant_Consumption")
conso2020 <- conso2020[,-c(4:5,2)]

#teleworking par pays 2019
teleworking2020 <- tab_R2.2.2010 %>% filter(TIME == 2020) %>% rename("teleworking2020"="Teleworking")
teleworking2020 <- teleworking2020[,-c(2:3,5)]


#pays avec le plus et le moins de telework 


teleworking.tophigh <- teleworking2020 %>% arrange(desc(teleworking2020)) 
teleworking.tophigh <- teleworking.tophigh[1:4,] %>% select(LOCATION,teleworking2020)


teleworking.toplow <- teleworking2020 %>% arrange(teleworking2020) 
teleworking.toplow <- teleworking.toplow[1:4,] %>% select(LOCATION,teleworking2020)


kbl(
  tibble(
    'Top Countries' = teleworking.tophigh$LOCATION,
    "TTeleworking " = teleworking.tophigh$teleworking2020,
    'Low Countries' = teleworking.toplow$LOCATION,
    "LTeleworking" = teleworking.toplow$teleworking2020
  ),
  caption = "**Table 3**: countries with the most and least teleworkers 2020",
  align = c("lclc")
) %>%
  kable_classic(full_width = T, html_font = "Cambria") %>%
  kable_styling(bootstrap_options = c('striped', 'hover', 'condensed'),table.envir = "table") %>%
  column_spec(c(1,3), width = "8cm")


#tableau antidepressant conso pour top tele

List.top.telework <- c("PRT","ITA","ESP","ISL")
List.low.telework <- c("HUN","NOR","GRC")

tableau.top.conso4 <-  conso2020 %>%filter(LOCATION %in% List.top.telework) %>% arrange(desc(conso2020)) 
mean.top.consumption2020 <- mean(tableau.top.conso4$conso2020)

tableau.low.conso4 <- conso2020 %>% filter(LOCATION %in% List.low.telework)  %>% arrange(desc(conso2020))
mean.low.consumption2020 <- mean(tableau.low.conso4$conso2020)


#tableau.low.conso2 %>% mutate(LOCATION= fct_reorder(LOCATION,conso)) #mettre ordre décroissant ? 

plot13 <-ggplot(data=tableau.top.conso4)+
  geom_bar(aes(x = conso2020, y= LOCATION),fill = '#0099CC',stat = "identity")+
  geom_text(aes(x = conso2020, y = LOCATION, label = paste(round(conso2020, digits = 2),"u")),
            hjust = 1.15,color='white')+
  ylab("top teleworking")+
  xlab("") +
  xlim(c(0,170))

plot14 <-ggplot(data=tableau.low.conso4)+
  geom_bar(aes(x = conso2020, y= LOCATION),fill = '#FF3399',stat = "identity")+
  geom_text(aes(x = conso2020, y = LOCATION, label = paste(round(conso2020, digits = 2),"u")),
            hjust = 1.15,color='white')+
  ylab("low teleworking")+
  xlab("") +
  xlim(c(0,170))

ggarrange(plot13,plot14,nrow = 2,align = 'v') %>%
  annotate_figure(top = text_grob("Antidepressant consumption For Countries with The Most and Least teleworkers in 2020", 
                                  size = 12),
                  bottom = text_grob("Antidepressant consumption"))

kbl(tibble(
  'Top Teleworking countries'=mean.top.consumption2020,
  'Low Teleworking countries'=mean.low.consumption2020
),
caption = "**Antidepressant consumption in countries with highest and lowest teleworking in 2020 **",
align = c("cc")
) %>%
  kable_classic(full_width = T, html_font = "Cambria") %>%
  kable_styling(bootstrap_options = c('striped', 'hover', 'condensed'),table.envir = "table")
```

# Public Spending on health analysis
First statistical analysis
Study of the first regression

```{r, echo = FALSE, message = FALSE}
Regression.total.tab_1 <- lm(tab_1$Value_Spending.on.health ~ tab_1$Mental_health_Value + tab_1$Time + tab_1$Region) 
```
```{r}
summary(Regression.total.tab_1)
```
As a result, we have a model that looks viable. The percentage of variance explained is 68%, and the p-value is extremely low. Moreover, the the dependent variable 'Value spending on health' is significantly correlated to:
'Mental Health value', 
'Time', 
'RegionNorth America', 
'RegionOceania', 
‘RegionWestern Europe'

TEST OF CLUSTERS
To better understand the distribution of these values, we represent them by clusters.
First we standardize the data
Normalize data
Computation of the euclidienne distance
We create the Cluster Dendogram
We calculate the average clusters

```{r}
data_test <- tab_2[-c(1,2,3)]
data_test <- data_test[,c(2,1)]
mean_data <-apply(data_test, 2, mean)
mean_data
std <- apply(data_test,2,sd)
data_test_std <- scale(data_test, mean_data,std)
row.names(data_test_std) <- tab_2[,2]
data_test_std
distance <- dist(data_test_std)
distance
print(distance, digits = 1)
hc <- hclust(distance)
plot(hc, labels= tab_2$Entity)
```
Then we use an average-linkage model on the scaled data and use 5 clusters to show the difference:
Study what is the optimal number of clusters k that is relevant to use
We conclude that a number of 5 clusters is optimal because the total within the sum of squares reduces only slightly from this point.
Graphical representation of the clusters

```{r}
avclust <- hclust(distance, method='average')
plot(avclust, labels=tab_2$Entity)

ct1 <- cutree(avclust, k=5)
plot(avclust, labels=tab_2$Entity) 
rect.hclust(avclust, k=5, border="red")
fviz_nbclust(data_test_std, kmeans, method="wss")
km.res <- kmeans(data_test_std, 5)
fviz_cluster(km.res, data=data_test_std, repel=TRUE)
```
We can observe the different distribution of the values according to the country's structures. The countries are distributed according to the location

Multilevel analysis
This multilevel analysis gives the opportunity to observe how the model can adapt to clusters, in this case to the 'Region' from tab_1. 
We want to add the regression to each Region.

```{r}
ggplot(tab_1, aes(x=Mental_health_Value, y=Value_Spending.on.health)) +
  geom_point() +
  facet_wrap(~Region)

tab_1$Mental_health_Value2 <- scale(tab_1$Mental_health_Value, center=TRUE, scale=TRUE) 

rd.int <- lmer(Value_Spending.on.health ~ Mental_health_Value2 + (1|Region), data=tab_1) 
summary(rd.int)

rd.int.sl <- lmer(Value_Spending.on.health ~ Mental_health_Value2 + (1 + Mental_health_Value2|Region), data = tab_1)

summary(rd.int.sl)

ggplot(tab_1, aes(x = Mental_health_Value, y = Value_Spending.on.health)) +
  facet_wrap(~Region, nrow=2) +
  geom_point(alpha = 0.5) +
  geom_line(data = cbind(tab_1, pred = predict(rd.int.sl)), aes(y = pred), size = 1, color='red')


lmtest <- lm(tab_1$Value_Spending.on.health ~ tab_1$Mental_health_Value2 + factor(tab_1$Region))

summary(lmtest)
```

As specified and checked by these plots, the slopes are now varying across observations of regions and so are the respective intercepts. 
We can really identify the clusters that are created with this analysis. Indeed we can observe that Oceania's countries have the highest prevalence of mental illness.
That is really the value added of this model, in that we want to control for the fact that we have different populations in order to determine the “true” relationship between 'mental illness' proportion and 'public spending on health'.
Looking at Asia, there  is a positive correlation between Mental health disorder prevalence and value spending on health.This aspect is also verified with Eastern Europe, and North America.
However the interpretation of Northern Europe, Oceania, South America and Western Europe is different because the slope coefficient is close to zero. 
In conclusion it means that indeed in overall, by pooling all the data together, our two variables X and Y are significantly, positively correlated.
But after a multilevel analysis, by Region, we understand that the positive correlation is less present looking into one specific Region. It means that the location has a big impact on these values. 

→ To conclude, The 'Value_Spending.on.health' is positively correlated to 'Mental_Health_Value' and to 'Time'. However the countries that are part of the same location are more likely to have the same values, especially in Northern Europe, Oceania, South America and Western Europe. 
In these regions, it is more difficult to conclude about the impact of ‘mental health disorder prevalence’ on the ‘value spending on health’.


→ Therefore, locality impacts Mental Health values and we cannot explain 100% of the variation in these values with the working environment of a country.






















