---
title: "Analysis"
output: html_document
---
# Analysis

```{r, echo = FALSE, message = FALSE}
source(here::here("scripts/Setup.R"))
```

 
## Question 1 : Mental health through the work environment

We decide to do a cluster analysis to see if there is some prevalence of certain region compared to others, and also wanted to study our problem through another perspective, that of the countries. Indeed, we could notice on the first plots, some countries adopt more extreme behaviors (position separated from the others) and it is often the same across the different variables.  A good way to analyze this is to group our countries using clusters. The goal is to see if the work environment has more impact in some countries
than in others on the mental health of its population. This is also where we will use our table of averages that we made for each of the variables.

```{r, echo = FALSE, message = FALSE}
# We remove the NA because we don't want to have biais in our cluster analysis 
tab_mean_na <- na.omit(tab_mean)
```
### Cluster analysis for each of our explanatory variables
```{r}
# Income Inequality
data_t0 <- tab_mean_na[-1]
data_t0 <- data_t0[,c(2,1)]
mean_data <- apply(data_t0, 2, mean)
std <- apply(data_t0,2,sd)
data_t0_std <- scale(data_t0, mean_data, std)
row.names(data_t0_std) <- tab_mean_na[,1]
distance <- dist(data_t0_std)
hc <- hclust(distance)
avclust <- hclust(distance, method = "average")
km.res <- kmeans(data_t0_std, 5)
C0 <- fviz_cluster(km.res, data=data_t0_std, repel = TRUE) 

# Wages
data_t1 <- tab_mean_na[-1]
data_t1 <- data_t1[,c(3,1)]
mean_data <- apply(data_t1, 2, mean)
std <- apply(data_t1,2,sd)
data_t1_std <- scale(data_t1, mean_data, std)
row.names(data_t1_std) <- tab_mean_na[,1]
distance <- dist(data_t1_std)
hc <- hclust(distance)
avclust <- hclust(distance, method = "average")
km.res <- kmeans(data_t1_std, 5)
C1 <- fviz_cluster(km.res, data=data_t1_std, repel = TRUE)

# Unemployment
data_t2 <- tab_mean_na[-1]
data_t2 <- data_t2[,c(4,1)]
mean_data <- apply(data_t2, 2, mean)
std <- apply(data_t2,2,sd)
data_t2_std <- scale(data_t2, mean_data, std)
row.names(data_t2_std) <- tab_mean_na[,1]
distance <- dist(data_t2_std)
hc <- hclust(distance)
avclust <- hclust(distance, method = "average")
km.res <- kmeans(data_t2_std, 5)
C2 <- fviz_cluster(km.res, data=data_t2_std, repel = TRUE)

# Working Age
data_t3 <- tab_mean_na[-1]
data_t3 <- data_t3[,c(5,1)]
mean_data <- apply(data_t3, 2, mean)
std <- apply(data_t3,2,sd)
data_t3_std <- scale(data_t3, mean_data, std)
row.names(data_t3_std) <- tab_mean_na[,1]
distance <- dist(data_t3_std)
hc <- hclust(distance)
avclust <- hclust(distance, method = "average")
km.res <- kmeans(data_t3_std, 5)
C3 <- fviz_cluster(km.res, data=data_t3_std, repel = TRUE)

# GDP
data_t5 <- tab_mean_na[-1]
data_t5 <- data_t5[,c(7,1)]
mean_data <- apply(data_t5, 2, mean)
std <- apply(data_t5,2,sd)
data_t5_std <- scale(data_t5, mean_data, std)
row.names(data_t5_std) <- tab_mean_na[,1]
distance <- dist(data_t5_std)
hc <- hclust(distance)
avclust <- hclust(distance, method = "average")
km.res <- kmeans(data_t5_std, 5)
C4 <- fviz_cluster(km.res, data=data_t5_std, repel = TRUE)

# Put all the graphs together
plot_grid(C0, C1, C2, C3, C4, labels=c("A","B","C","D","E","F"), ncol=3, nrow=2)
```

This graph shows us that, regardless of the work environment variable, we always have a clear demarcation. Indeed, it is always the same countries in the same places. We can therefore conclude that each region has its own specificities related to the work environment that impact the rate of mental health disorders. 

It would therefore be interesting to see how these behave according to the regions. 

```{r, echo = FALSE, message = FALSE}
mod2 <- lm(tab$Mental_Health ~ tab$Region + tab$TIME)
summary(mod2)
```

Our model is significant in all regions studied. 

----


## Question 2 : ??? Covid 

#### Antidepressant use and Covid


```{r, echo = FALSE, message = FALSE}

cor(tab_R2.1$Antidepressant_Consumption, tab_R2.1$Deaths)
cor(tab_R2.1$Antidepressant_Consumption, tab_R2.1$Cases)
```

We obtain a correlation of "0,049" between antidepressant consumption and the number of deaths due to covid, and a correlation of "0,0453" between antidepressant consumption and Covid cases.  

Unfortunately, we can see that there is no correlation between these variables, either with the number of cases or the number of deaths. 
We can give several explanations to this surprising observation.

The first one is the lack of data. Indeed, we were able to study the evolution of antidepressant consumption in only 8 countries. Perhaps with more countries, we would have seen a more significant difference. 

The second and the most likely, is that we can see that the number of cases (and deaths) related to covid are huge numbers, going from 0 to several millions (to thousands). However, compared to these numbers, the value of antidepressants consumption is increasing well as we can see in the graph below but not as much as the number of cases. The ratio is not the same. 

We will now calculate the value of the increase in antidepressant consumption, by years and see if we can observe a difference between years or not, and compare it to the value of the consumption in 2020.  

```{r, echo = FALSE, message = FALSE}
#Tableau antidepresseurs, croissance chaque année
tab_R2.1G <- ddply(Antidepressant_consumption2, .(LOCATION),
                                  function (d) {
                                    d$Growth <- c(NA, tail(d$Antidepressant_Consumption, -1) - head(d$Antidepressant_Consumption, -1))
                                    d
                                  }
)

#Tableau croissance jusqu'en 2019
tab_R2.1.2019 <- tab_R2.1G %>%
  group_by(LOCATION,Growth) %>%
  filter(TIME< 2020)

#Moyenne croissance jusqu'en 2019
tab_R2.1mean <-aggregate(tab_R2.1.2019[,4], list(tab_R2.1.2019$LOCATION), mean, na.rm=T)
tab_R2.1mean <-rename(tab_R2.1mean, "LOCATION" = "Group.1")

#Tableau conso 2020 et croissance entre 2019 et 2020
tab_R2.1.G2020 <- tab_R2.1G %>%
  group_by(LOCATION,Growth) %>%
  filter(TIME == 2020)
  
#Tableau croissance entre 2019 et 2020
tab_R2.1.G2020 <-tab_R2.1.G2020[-3]

#Tableau moyenne croissance jusqu'en 2019 et croissance 2019/2020
comparaison <- merge(tab_R2.1mean,tab_R2.1.G2020, by = c("LOCATION"))
comparaison <- rename(comparaison, c("Growth_mean"="Growth.x","Growth2020"="Growth.y"))
comparaison <- comparaison[-3]

#Tableau moyenne conso jusqu'en 2019 
consumptionMean <- aggregate(tab_R2.1.2019[,3], list(tab_R2.1.2019$LOCATION), mean)
consumptionMean <-rename(consumptionMean, "LOCATION" = "Group.1")

#On ajoute conso moyenne a comparaison
comparaison <- merge(comparaison,consumptionMean, by = c("LOCATION"))
comparaison <- rename(comparaison,"Consumption_mean"="Antidepressant_Consumption")

#Tableau Conso 2020
consumption2020 <- tab_R2.1 %>%
  group_by(LOCATION,Antidepressant_Consumption) %>%
  filter(TIME == 2020)


#On ajoute conso 2020 a comparaison 
comparaison <- merge(comparaison,consumption2020, by = c("LOCATION"))
comparaison <- rename(comparaison,"Consumption2020"="Antidepressant_Consumption")
comparaison <- comparaison[,-c(5,6,7)]

kbl(comparaison,caption = "**Table 1: **Table by country of antidepressant consumption in 2020, its growth between 2019 and 2020, compared to the average antidepressant consumption and growth of previous years.") %>%
  kable_classic(full_width = T, html_font = "Cambria") %>%
  kable_styling(bootstrap_options = c('striped', 'hover', 'condensed'))

```

When we calculate the average antidepressant consumption from 2000 to 2019 and compare it to the consumption in 2020 we notice that the latter is for all countries higher than the average of the previous years. 
Then, when we compare the average growth in consumption per year, to the growth between 2019 and 2020, we see that the latter is higher than the average for 5 of the 8 countries analyzed (Portugal, Italy, Iceland, Hungary and Greece). 

This shows that the consumption of antidepressants has increased in 2020, which could be well explained by the covid crisis. 

##### Depression Rate and Covid

We will try to demonstrate a link between the Covid crisis and the depression rate in our selection of countries. 
To do this, we classified the countries into two categories: the countries with the most Covid deaths (which we therefore consider the most affected by the crisis) and the countries with the least Covid deaths. Next, we will compare the depression rates of countries in 2021 according to these two categories. 
It is true that in this table we are comparing data from 2 different years : we only have the depression rate in 2021, and the Covid data we have is only in 2020.
However, for our study, we did not consider this as a problem, on the contrary. Indeed, knowing that the Covid crisis is still happening today and that the effects of a crisis are often felt some time afterwards, we believe that the analysis of the 2021 depression rate is relevant to show if there are any effects of the covid crisis.


```{r, echo = FALSE, message = FALSE}
covid <- Number_Covid19_cases_deaths %>%
  filter(LOCATION %in% List.of.Countries)

deaths.tophigh <- covid %>% arrange(desc(Deaths)) 
deaths.tophigh <- deaths.tophigh[1:13,] %>% select(LOCATION,Deaths)

deaths.toplow <- covid %>% arrange(Deaths) 
deaths.toplow <- deaths.toplow[1:13,] %>% select(LOCATION,Deaths)


kbl(
  tibble(
    'Top Countries' = deaths.tophigh$LOCATION,
    "TCDeaths " = deaths.tophigh$Deaths,
    'Low Countries' = deaths.toplow$LOCATION,
    "LDeaths" = deaths.toplow$Deaths
  ),
  caption = "**Table 1**: countries with the most and least deaths of covid in 2020 .",
  align = c("lclc")
) %>%
  kable_classic(full_width = T, html_font = "Cambria") %>%
  kable_styling(bootstrap_options = c('striped', 'hover', 'condensed'),table.envir = "table") %>%
  column_spec(c(1,3), width = "8cm")




List.top.deaths <- c("HUN","CZE","BRA","ROU","HRV","BEL","USA","ITA","POL","ESP","FRA","PRT","GRC")
List.low.deaths <- c("CHN","NZL","AUS","ISL","JPN","NOR","FIN","CAN","NLD","DEU","AUT","CHE","SWE")

tableau.top.deaths <-  Depression_Rate2021 [-3]%>%filter(LOCATION %in% List.top.deaths) 
mean.top.rate.deaths <- mean(tableau.top.deaths$Depression_Rate)

tableau.low.deaths <- Depression_Rate2021 [-3]%>% filter(LOCATION %in% List.low.deaths)
mean.low.rate.deaths <- mean(tableau.low.deaths$Depression_Rate)

plot3 <- ggplot(data=tableau.top.deaths)+
  geom_bar(aes(x = Depression_Rate, y= reorder(LOCATION,Depression_Rate)),fill = '#0099CC',stat = "identity")+
  geom_text(aes(x = Depression_Rate, y = reorder(LOCATION,Depression_Rate), label = paste(round(Depression_Rate, digits = 2),"%")),
            hjust = 1.15,color='white')+
  ylab("top Covid Deaths")+
  xlab("") +
  xlim(c(0,6))


plot4 <- ggplot(data=tableau.low.deaths)+
  geom_bar(aes(x = Depression_Rate, y= reorder(LOCATION,Depression_Rate)),fill = '#FF3399',stat = "identity")+
  geom_text(aes(x = Depression_Rate, y = reorder(LOCATION,Depression_Rate), label = paste(round(Depression_Rate, digits = 2),"%")),
            hjust = 1.15,color='white')+
  ylab("low Covid Deaths")+
  xlab("") +
  xlim(c(0,6))

ggarrange(plot3,plot4,nrow = 2,align = 'v') %>%
  annotate_figure(top = text_grob("Depression Rate For Countries with The Most and Least deaths of Covid in 2020", 
                                  size = 12),
                  bottom = text_grob("Depression Rate"))

kbl(tibble(
  'Top Covid deaths'=mean.top.rate.deaths,
  'Low Covid deaths'=mean.low.rate.deaths
),
caption = "**Average depression rate in countries with highest and lowest Covid-19 Deaths**",
align = c("cc")
) %>%
  kable_classic(full_width = T, html_font = "Cambria") %>%
  kable_styling(bootstrap_options = c('striped', 'hover', 'condensed'),table.envir = "table")
```
Our results do not show a clearly visible difference graphically since the highest value for both graphs is 5.9%. The scope, however, is different. For countries with the most covid deaths the value goes down to 4.8% for Belgium while it goes down to 4.1% for Iceland in the second graph.
Moreover, when calculating the average of the depression rates of countries classified in the category with the most and least Covid deaths, we can see a slight difference. Indeed, countries that were "most affected by Covid" (with the most deaths), have, on average, a higher depression rate (5,27%) than countries with the fewest deaths from Covid (4,9%). 



##### Antidepressant consumption and teleworking

We will now focus our analysis on changes in antidepressant use as a function of telecommuting. We will see if there is a relationship between these variables.

```{r, echo = FALSE, message = FALSE}
g.teleworking.consumption <- ggplot(data = tab_R2.2, mapping = aes(x = Teleworking, y = Antidepressant_Consumption)) +
  geom_point(mapping = aes(color = LOCATION)) +
  #geom_smooth()+
  ylim(0,160)+
  xlim(0,15)+
  ggtitle("Evolution of antidepressant consumption according to the percentage of teleworking by country") +
  xlab("Teleworking in % of workers") + ylab("Antidepressant Consumption") 
ggplotly(g.teleworking.consumption)
```

Here is a graph that shows how the value of antidepressant consumption varies with teleworking. Each color represents a country. There is no evidence of an increase in antidepressant use when there are more teleworkers, for all countries, but for some there is.
Indeed, we can observe an increase for the Netherlands, Switzerland or Spain for example but there is no upward trend for all.  

Therefore, for the rest of the analysis, we will determine two lists of countries. The first list will contain the countries with the most teleworkers in % of the active population, on average between 2010 and 2020 (above 5%) and the second one, the countries with a lower average rate.

### Countries with the most and least teleworkers on AVERAGE compared to antidepressant consumption 

```{r, echo = FALSE, message = FALSE}
tab_R2.2.2010 <- tab_R2.2 %>% filter(TIME > 2009)
#moyenne consommation antidepresseur par pays
mean.conso <- aggregate(tab_R2.2.2010[, 3], list(tab_R2.2.2010$LOCATION), mean)
mean.conso <- rename(mean.conso, c("LOCATION" = "Group.1","conso"="x"))

#moyenne teleworking par pays 
mean.teleworking <- aggregate(tab_R2.2.2010[, 4], list(tab_R2.2.2010$LOCATION), mean, na.rm=T)
mean.teleworking <- rename(mean.teleworking, c("LOCATION" = "Group.1","teleworking"="x"))


#pays avec le plus et le moins de telework 


teleworking.tophigh <- mean.teleworking %>% arrange(desc(teleworking)) 
teleworking.tophigh <- teleworking.tophigh[1:8,] %>% select(LOCATION,teleworking)

teleworking.toplow <- mean.teleworking %>% arrange(teleworking) 
teleworking.toplow <- teleworking.toplow[1:8,] %>% select(LOCATION,teleworking)


kbl(
  tibble(
    'Top Countries' = teleworking.tophigh$LOCATION,
    "TTeleworking " = teleworking.tophigh$teleworking,
    'Low Countries' = teleworking.toplow$LOCATION,
    "LTeleworking" = teleworking.toplow$teleworking
  ),
  caption = "**Table 2**: countries with the most and least teleworkers **on average** from 2010 to 2019",
  align = c("lclc")
) %>%
  kable_classic(full_width = T, html_font = "Cambria") %>%
  kable_styling(bootstrap_options = c('striped', 'hover', 'condensed'),table.envir = "table") %>%
  column_spec(c(1,3), width = "8cm")

```

The table above includes Sweden in both lists (top and low teleworking) because we have 15 countries (an odd number) and it is not possible to build a table with a different number of rows for the 2 columns. When this is the case, we assume that the top list includes one more country. So, Sweden (SWE) will be counted only in the first list (top teleworking) to realize the following bar plot. 

```{r, echo = FALSE, message = FALSE}

#tableau antidepressant conso pour top tele

List.top.telework <- c("NLD","FIN","DNK","AUT","BEL","ISL","PRT","SWE")
List.low.telework <- c("HUN","GRC","CZE","DEU","ITA","ESP","NOR")

tableau.top.conso2 <-  mean.conso %>%filter(LOCATION %in% List.top.telework) %>% arrange(desc(conso)) 

mean.top.consumption <- mean(tableau.top.conso2$conso)

tableau.low.conso2 <- mean.conso %>% filter(LOCATION %in% List.low.telework)  %>% arrange(desc(conso))
mean.low.consumption <- mean(tableau.low.conso2$conso)



plot9 <-ggplot(data=tableau.top.conso2)+
  geom_bar(aes(x = conso, y= reorder(LOCATION,conso)),fill = '#0099CC',stat = "identity")+
  geom_text(aes(x = conso, y = reorder(LOCATION,conso), label = paste(round(conso, digits = 2),"u")),
            hjust = 1.15,color='white')+
  ylab("top teleworking")+
  xlab("") +
  xlim(c(0,150))


#tableau antidepressant conso pour low tele

plot10 <-ggplot(data=tableau.low.conso2)+
  geom_bar(aes(x = conso, y= reorder(LOCATION,conso)),fill = '#FF3399',stat = "identity")+
  geom_text(aes(x = conso, y = reorder(LOCATION,conso), label = paste(round(conso, digits = 2),"u")),
            hjust = 1.15,color='white')+
  ylab("low teleworking")+
  xlab("") +
  xlim(c(0,150))

ggarrange(plot9,plot10,nrow = 2,align = 'v') %>%
  annotate_figure(top = text_grob("Antidepressant consumption For Countries with The Most and Least teleworkers on average 2010/2019", 
                                  size = 9),
                  bottom = text_grob("Antidepressant consumption"))

kbl(tibble(
  'Top Teleworking countries'=mean.top.consumption,
  'Low Teleworking countries'=mean.low.consumption
),
caption = "**Average Antidepressant consumption in countries with highest and lowest teleworking**",
align = c("cc")
) %>%
  kable_classic(full_width = T, html_font = "Cambria") %>%
  kable_styling(bootstrap_options = c('striped', 'hover', 'condensed'),table.envir = "table")
```

The two graphs above show a significant difference between the two country selections. Indeed, the average antidepressant consumption of the countries with the most teleworking is 80.4 compared to only 51.5 for the average of the countries with the least teleworking.
Moreover, in the second list of countries (low teleworking), all countries (7 countries) have a consumption of antidepressants lower than 72.87 while in the first list only 3 have a consumption lower than this figure. In fact, the majority (5 out of 8) have a consumption of more than 70, with Iceland recording a consumption of 125 doses per day.  

With this 10 year average, we can already see a potential connection between these two variables. Indeed, the countries with the most teleworkers also seem to be the countries with the highest consumption of antidepressants per 100 inhabitants per day. 

To complete our analysis, and to avoid potentially biased results by the average, we will also focus on a single year. We will compare antidepressant use in the countries with the highest and lowest rates of teleworking in 2020, the year of the covid.


```{r, echo = FALSE, message = FALSE}
#consommation antidepresseur par pays
conso2020 <- tab_R2.2.2010 %>% filter(TIME == 2020) %>% rename("conso2020"="Antidepressant_Consumption")
conso2020 <- conso2020[,-c(4:5,2)]

#teleworking par pays 2019
teleworking2020 <- tab_R2.2.2010 %>% filter(TIME == 2020) %>% rename("teleworking2020"="Teleworking")
teleworking2020 <- teleworking2020[,-c(2:3,5)]


#pays avec le plus et le moins de telework 


teleworking.tophigh <- teleworking2020 %>% arrange(desc(teleworking2020)) 
teleworking.tophigh <- teleworking.tophigh[1:4,] %>% select(LOCATION,teleworking2020)


teleworking.toplow <- teleworking2020 %>% arrange(teleworking2020) 
teleworking.toplow <- teleworking.toplow[1:4,] %>% select(LOCATION,teleworking2020)


kbl(
  tibble(
    'Top Countries' = teleworking.tophigh$LOCATION,
    "TTeleworking " = teleworking.tophigh$teleworking2020,
    'Low Countries' = teleworking.toplow$LOCATION,
    "LTeleworking" = teleworking.toplow$teleworking2020
  ),
  caption = "**Table 3**: countries with the most and least teleworkers 2020",
  align = c("lclc")
) %>%
  kable_classic(full_width = T, html_font = "Cambria") %>%
  kable_styling(bootstrap_options = c('striped', 'hover', 'condensed'),table.envir = "table") %>%
  column_spec(c(1,3), width = "8cm") 
```

The table above includes Iceland in both lists (top and low teleworking) because we have again an odd number of countries (7) and it is not possible to build a table with a different number of rows for the 2 columns. We therefore assume that the top list includes one more country. So, Iceland (ISL) will be counted only in the first list (top teleworking) to realize the following bar plot. 


```{r, echo = FALSE, message = FALSE}
#tableau antidepressant conso pour top tele

List.top.telework <- c("PRT","ITA","ESP","ISL")
List.low.telework <- c("HUN","NOR","GRC")

tableau.top.conso4 <-  conso2020 %>%filter(LOCATION %in% List.top.telework) %>% arrange(desc(conso2020)) 
mean.top.consumption2020 <- mean(tableau.top.conso4$conso2020)

tableau.low.conso4 <- conso2020 %>% filter(LOCATION %in% List.low.telework)  %>% arrange(desc(conso2020))
mean.low.consumption2020 <- mean(tableau.low.conso4$conso2020)



plot13 <-ggplot(data=tableau.top.conso4)+
  geom_bar(aes(x = conso2020, y= reorder(LOCATION,conso2020)),fill = '#0099CC',stat = "identity")+
  geom_text(aes(x = conso2020, y = reorder(LOCATION,conso2020), label = paste(round(conso2020, digits = 2),"u")),
            hjust = 1.15,color='white')+
  ylab("top teleworking")+
  xlab("") +
  xlim(c(0,170))

plot14 <-ggplot(data=tableau.low.conso4)+
  geom_bar(aes(x = conso2020, y= reorder(LOCATION,conso2020)),fill = '#FF3399',stat = "identity")+
  geom_text(aes(x = conso2020, y = reorder(LOCATION,conso2020), label = paste(round(conso2020, digits = 2),"u")),
            hjust = 1.15,color='white')+
  ylab("low teleworking")+
  xlab("") +
  xlim(c(0,170))

ggarrange(plot13,plot14,nrow = 2,align = 'v') %>%
  annotate_figure(top = text_grob("Antidepressant consumption For Countries with The Most and Least teleworkers **in 2020**", 
                                  size = 12),
                  bottom = text_grob("Antidepressant consumption"))

kbl(tibble(
  'Top Teleworking countries'=mean.top.consumption2020,
  'Low Teleworking countries'=mean.low.consumption2020
),
caption = "**Antidepressant consumption in countries with highest and lowest teleworking in 2020 **",
align = c("cc")
) %>%
  kable_classic(full_width = T, html_font = "Cambria") %>%
  kable_styling(bootstrap_options = c('striped', 'hover', 'condensed'),table.envir = "table")
```

Despite the lack of data (observation only possible on 7 countries instead of 15 above), the results of this second analysis confirm what we thought. Indeed, the two averages are even further apart and the average antidepressant consumption for the countries with the highest teleworking rate (top teleworking) is twice as high as the average of this consumption for the second list (low teleworking).
Moreover, except for Italy, all countries in the first list (top teleworking) have a higher consumption of antidepressants than all the countries in the second list (low teleworking). 

Countries with the most teleworkers are therefore also the countries with the highest consumption of antidepressants per day. 

----

## Question 3 : ??? Public Spending on health analysis
First statistical analysis
Study of the first regression

```{r, echo = FALSE, message = FALSE}
Regression.total.tab_1 <- lm(tab_1$Value_Spending.on.health ~ tab_1$Mental_health_Value + tab_1$Time + tab_1$Region) 
```
```{r}
summary(Regression.total.tab_1)
```
As a result, we have a model that looks viable. The percentage of variance explained is 68%, and the p-value is extremely low. Moreover, the the dependent variable 'Value spending on health' is significantly correlated to:
'Mental Health value', 
'Time', 
'RegionNorth America', 
'RegionOceania', 
‘RegionWestern Europe'

TEST OF CLUSTERS
To better understand the distribution of these values, we represent them by clusters.
First we standardize the data
Normalize data
Computation of the euclidienne distance
We create the Cluster Dendogram
We calculate the average clusters

```{r}
data_test <- tab_2[-c(1,2,3)]
data_test <- data_test[,c(2,1)]
mean_data <-apply(data_test, 2, mean)
mean_data
std <- apply(data_test,2,sd)
data_test_std <- scale(data_test, mean_data,std)
row.names(data_test_std) <- tab_2[,2]
data_test_std
distance <- dist(data_test_std)
distance
print(distance, digits = 1)
hc <- hclust(distance)
plot(hc, labels= tab_2$Entity)
```
Then we use an average-linkage model on the scaled data and use 5 clusters to show the difference:
Study what is the optimal number of clusters k that is relevant to use
We conclude that a number of 5 clusters is optimal because the total within the sum of squares reduces only slightly from this point.
Graphical representation of the clusters

```{r}
avclust <- hclust(distance, method='average')
plot(avclust, labels=tab_2$Entity)

ct1 <- cutree(avclust, k=5)
plot(avclust, labels=tab_2$Entity) 
rect.hclust(avclust, k=5, border="red")
fviz_nbclust(data_test_std, kmeans, method="wss")
km.res <- kmeans(data_test_std, 5)
fviz_cluster(km.res, data=data_test_std, repel=TRUE)
```
We can observe the different distribution of the values according to the country's structures. The countries are distributed according to the location

Multilevel analysis
This multilevel analysis gives the opportunity to observe how the model can adapt to clusters, in this case to the 'Region' from tab_1. 
We want to add the regression to each Region.

```{r}
ggplot(tab_1, aes(x=Mental_health_Value, y=Value_Spending.on.health)) +
  geom_point() +
  facet_wrap(~Region)

tab_1$Mental_health_Value2 <- scale(tab_1$Mental_health_Value, center=TRUE, scale=TRUE) 

rd.int <- lmer(Value_Spending.on.health ~ Mental_health_Value2 + (1|Region), data=tab_1) 
summary(rd.int)

rd.int.sl <- lmer(Value_Spending.on.health ~ Mental_health_Value2 + (1 + Mental_health_Value2|Region), data = tab_1)

summary(rd.int.sl)

lmtest <- lm(tab_1$Value_Spending.on.health ~ tab_1$Mental_health_Value2 + factor(tab_1$Region))

summary(lmtest)
```

```{r}
ggplot(tab_1, aes(x = Mental_health_Value, y = Value_Spending.on.health)) +
  facet_wrap(~Region, nrow=2) +
  geom_point(alpha = 0.5) +
  geom_line(data = cbind(tab_1, pred = predict(rd.int.sl)), aes(y = pred), size = 1, color='red')

```

As specified and checked by these plots, the slopes are now varying across observations of regions and so are the respective intercepts. 
We can really identify the clusters that are created with this analysis. Indeed we can observe that Oceania's countries have the highest prevalence of mental illness.
That is really the value added of this model, in that we want to control for the fact that we have different populations in order to determine the “true” relationship between 'mental illness' proportion and 'public spending on health'.

To interpret this table (summary of rd.int.sl), consider the Regions(i) variables as dummy variables. The value takes 1 * coefficient when we analyse the region in question and 0 otherwise. For instance, if we focus on North America, the value takes 1 * 3.2304. It means that if we increase the mental health value of 1% in North america, according to these datas, the value of the senpding on health is increasing significantly by 3.2304%.

Looking at Asia, there  is a positive correlation between Mental health disorder prevalence and value spending on health.This aspect is also verified with Eastern Europe, and North America.
However the interpretation of Northern Europe, Oceania, South America and Western Europe is different because the slope coefficient is close to zero. 
In conclusion it means that indeed in overall, by pooling all the data together, our two variables X and Y are significantly, positively correlated.
But after a multilevel analysis, by Region, we understand that the positive correlation is less present looking into one specific Region. It means that the location has a big impact on these values. 

→ To conclude, The 'Value_Spending.on.health' is positively correlated to 'Mental_Health_Value' and to 'Time'. However the countries that are part of the same location are more likely to have the same values, especially in Northern Europe, Oceania, South America and Western Europe. 
In these regions, it is more difficult to conclude about the impact of ‘mental health disorder prevalence’ on the ‘value spending on health’.


→ Therefore, locality impacts Mental Health values and we cannot explain 100% of the variation in these values with the working environment of a country.Finally, given that these two variables are not exogenous and positively correlated, we cannot say that there is a causal effect.





















