---
title: "Data"
output: html_document
---
# Data

First, we need to install different packages. 
```{r}
source(here::here("scripts/Setup.R"))
```
For our research, we are going to use different databases around our three themes: mental health in the work environment, during the covid period, and public spending on health. 

## Question 1 : Mental health through the work environment 

First of all, for the database concerning the environment at work, we have extracted all the data from the sites : <https://www.oecd.org> and <https://ourworldindata.org>. 


Our first resarch question was : Given the structure of the working environment in different countries, can we say that the mental health of the population is influenced by the working conditions and the situation of the country?

To see those effects, we have chosen the information of 6 independants variables ; 

- the average work-time (Hours/worker)
- the GPD (US dollars/capita)
- the unemployment rate (% of labour force)
- the working age population (% of population)
- the average wages (US dollars)
- the income inequalities (Gini coefficient, 0=complete equality and 1=complete inequality)

$$Analysis 1 : MentalHealth = a*IncomeInequality + b*wages + c*Unemployment + d*WorkingAgePopulation + e*WorkTime + f*GPD$$

We have made a selection of several countries which are the following (To simplify, country codes have been used and not the full names) : Austria, Belgium, Croatia, Czechia, Denmark, Finland, France, Germany, Greece, Hungary, Iceland, Ireland, Italy, Romania, Portugal, Poland, Norway, Netherlands, Switzerland, Sweden, Spain, Australia, Brazil, Canada, Japan, New-Zealand and the USA.  

```{r}
tab_countries <- read.csv2(here::here("Data/Entities_LOCATION_Region.csv"))
```
We also sort these countries by their region.

```{r}
List.of.Countries = c('AUT','BEL','HRV', 'CZE', 'DNK', 'ENG', 'FIN', 'FRA', 'DEU', 'GRC', 'HUN', 'ISL', 'ITA', 'ROU', 'PRT', 'POL', 'NOR', 'NLD', 'CHE', 'SWE', 'ESP', 'AUS', 'BRA', 'CAN', 'JPN', 'NZL', 'USA')
```


```{r}
kbl(tab_countries,caption = "**Table of OCDE countries**: `tab_countries`, list of OCDE countries availabe in our dataset.") %>%
  kable_classic(full_width = T, html_font = "Cambria") %>%
  kable_styling(bootstrap_options = c('striped', 'hover', 'condensed'))
```

Now that we have collected all our data, we need to sort, order and rename them in order to obtain only tables with three columns to have the value of our variable according to its country and its date. We took the data for each of these variables for a certain sample of countries and then chose to do an individual average over the years from 2000 to 2017.


```{r}
Mental_Health <- read.csv(here::here("Data/Mental_Health.csv"))
attach(Mental_Health)
Mental_Health <- Mental_Health[,-1]
Mental_Health <- rename(Mental_Health,c("LOCATION"="Code", "TIME"="Year","ValueH"="Prevalence...Mental.and.substance.use.disorders...Sex..Both...Age..Age.standardized..Percent."))
List.of.Countries = c('AUT','BEL','HRV', 'CZE', 'DNK', 'ENG', 'FIN', 'FRA', 'DEU', 'GRC', 'HUN', 'ISL', 'ITA', 'ROU', 'PRT', 'POL', 'NOR', 'NLD', 'CHE', 'SWE', 'ESP', 'AUS', 'BRA', 'CAN', 'JPN', 'NZL', 'USA')
Mental_Health <-  Mental_Health %>% filter(LOCATION %in% List.of.Countries)
Mental_Health <- Mental_Health %>%
  filter(TIME>1999, TIME< 2018) 
Mental_Health <-  rename(Mental_Health,c("Mental_Health"="ValueH"))
Mental_Health$"TIME" <- as.integer(Mental_Health$"TIME")

Income_Inequality <- read.csv2(here::here("Data/Income_inequality-1.csv"))
attach(Income_Inequality)
Income_Inequality <- Income_Inequality[,-c(2:5,8)]
Income_Inequality$Value <- as.numeric(Income_Inequality$Value)
List.of.Countries = c('AUT','BEL','HRV', 'CZE', 'DNK', 'ENG', 'FIN', 'FRA', 'DEU', 'GRC', 'HUN', 'ISL', 'ITA', 'ROU', 'PRT', 'POL', 'NOR', 'NLD', 'CHE', 'SWE', 'ESP', 'AUS', 'BRA', 'CAN', 'JPN', 'NZL', 'USA')
Income_Inequality <-  Income_Inequality %>% filter(LOCATION %in% List.of.Countries)
Income_Inequality <- Income_Inequality %>%
  filter(TIME>1999, TIME< 2018)
Income_Inequality <- rename(Income_Inequality,c("Income_Inequality"="Value"))

wages <- read.csv(here::here("Data/Average_wages.csv"))
attach(wages)
wages <- wages[,-c(2:5,8)]
List.of.Countries = c('AUT','BEL','HRV', 'CZE', 'DNK', 'ENG', 'FIN', 'FRA', 'DEU', 'GRC', 'HUN', 'ISL', 'ITA', 'ROU', 'PRT', 'POL', 'NOR', 'NLD', 'CHE', 'SWE', 'ESP', 'AUS', 'BRA', 'CAN', 'JPN', 'NZL', 'USA')
wages <-  wages %>% filter(LOCATION %in% List.of.Countries)
wages <- wages %>%
  filter(TIME>1999, TIME< 2018)
wages <- rename(wages,c("Wages"="Value"))

Unemployment <- read.csv(here::here("Data/Unemployement_Rate1.csv"))
attach(Unemployment)
Unemployment <- Unemployment[,-c(2:5,8)]
List.of.Countries = c('AUT','BEL','HRV', 'CZE', 'DNK', 'ENG', 'FIN', 'FRA', 'DEU', 'GRC', 'HUN', 'ISL', 'ITA', 'ROU', 'PRT', 'POL', 'NOR', 'NLD', 'CHE', 'SWE', 'ESP', 'AUS', 'BRA', 'CAN', 'JPN', 'NZL', 'USA')
Unemployment <-  Unemployment %>% filter(LOCATION %in% List.of.Countries)
Unemployment <- Unemployment %>%
  filter(TIME>1999, TIME< 2018)
Unemployment <- rename(Unemployment,c("Unemployment"="Value"))

Working_Age <- read.csv(here::here("Data/Working_age_population.csv"))
attach(Working_Age)
Working_Age <- Working_Age[,-c(2:5,8)]
List.of.Countries = c('AUT','BEL','HRV', 'CZE', 'DNK', 'ENG', 'FIN', 'FRA', 'DEU', 'GRC', 'HUN', 'ISL', 'ITA', 'ROU', 'PRT', 'POL', 'NOR', 'NLD', 'CHE', 'SWE', 'ESP', 'AUS', 'BRA', 'CAN', 'JPN', 'NZL', 'USA')
Working_Age <-  Working_Age %>% filter(LOCATION %in% List.of.Countries)
Working_Age <- rename(Working_Age,c("Working_Age"="Value"))

Work_Time <- read.csv(here::here("Data/Avg_Work_Time.csv"))
attach(Work_Time)
Work_Time <- Work_Time[,-c(2:5,8)]
List.of.Countries = c('AUT','BEL','HRV', 'CZE', 'DNK', 'ENG', 'FIN', 'FRA', 'DEU', 'GRC', 'HUN', 'ISL', 'ITA', 'ROU', 'PRT', 'POL', 'NOR', 'NLD', 'CHE', 'SWE', 'ESP', 'AUS', 'BRA', 'CAN', 'JPN', 'NZL', 'USA')
Work_Time <-  Work_Time %>% filter(LOCATION %in% List.of.Countries)
Work_Time <- Work_Time %>%
  filter(TIME>1999, TIME< 2018) 
Work_Time <- rename(Work_Time,c("Work_Time"="Value"))

GDP <- read.csv(here::here("Data/gdp-per-capita.csv"))
attach(GDP)
GDP <- GDP[,-c(1,5)]
GDP <- rename(GDP,c("LOCATION"="Code", "TIME"="Year"))
List.of.Countries = c('AUT','BEL','HRV', 'CZE', 'DNK', 'ENG', 'FIN', 'FRA', 'DEU', 'GRC', 'HUN', 'ISL', 'ITA', 'ROU', 'PRT', 'POL', 'NOR', 'NLD', 'CHE', 'SWE', 'ESP', 'AUS', 'BRA', 'CAN', 'JPN', 'NZL', 'USA')
GDP <-  GDP %>% filter(LOCATION %in% List.of.Countries)
GDP <- GDP %>%
  filter(TIME>1999, TIME< 2018)
GDP <- rename(GDP,c("GDP"="GDP.per.capita"))
```

Now that we have all our variables in the right format, we need to put them in a common table so that we can have an overall representation and be able to observe and analyze the trends that emerge.

```{r}
tab_0 <- left_join(Mental_Health, Income_Inequality, by = c("LOCATION", "TIME"))
tab_1 <- left_join(tab_0, wages, by = c("LOCATION","TIME"))
tab_2 <- left_join(tab_1, Unemployment, by = c("LOCATION","TIME"))
tab_3 <- left_join(tab_2, Working_Age, by = c("LOCATION","TIME"))
tab_4 <- left_join(tab_3, Work_Time, by = c("LOCATION","TIME"))
tab_5 <- left_join(tab_4, GDP, by = c("LOCATION","TIME")) 
tab <- left_join(tab_5, tab_countries, by=('LOCATION'))
```

We need the values as numeric and not as characters for the analysis
```{r}
tab$LOCATION <- as.factor(tab$LOCATION)
tab$TIME <- as.numeric(tab$TIME)
```

```{r}
kbl(tab[1:20,],caption = "**Table 1.a : List of OECD countries common for all our data **: `tab`") %>%
  kable_classic(full_width = T, html_font = "Cambria") %>%
  kable_styling(bootstrap_options = c('striped', 'hover', 'condensed')) %>%
  add_footnote(
      paste(
         "Representation of the first 20 observation of the dataset. Total observations : ",
         nrow(tab)))
```

To see some other effects and to use clusters we will need an other table with the mean of each variable from year 2000 to 2017

```{r}
Mental_Health_m <- aggregate(Mental_Health[,3], list(Mental_Health$LOCATION), mean)
Mental_Health_m <- rename(Mental_Health_m,c("LOCATION"="Group.1","MentalHealth_mean"="x"))
Income_Inequality_m <- aggregate(Income_Inequality[,3], list(Income_Inequality$LOCATION), mean)
Income_Inequality_m <- rename(Income_Inequality_m,c("LOCATION"="Group.1","IncomeInequality_mean"="x"))
wages_m <- aggregate(wages[,3], list(wages$LOCATION), mean)
wages_m <- rename(wages_m,c("LOCATION"="Group.1","Wages_mean"="x"))
Unemployment_m <- aggregate(Unemployment[,3], list(Unemployment$LOCATION), mean)
Unemployment_m <- rename(Unemployment_m,c("LOCATION"="Group.1","Unemployment_mean"="x"))
Working_Age_m <- aggregate(Working_Age[,3], list(Working_Age$LOCATION), mean)
Working_Age_m <- rename(Working_Age_m,c("LOCATION"="Group.1","WorkingAge_mean"="x"))
Work_Time_m <- aggregate(Work_Time[,3], list(Work_Time$LOCATION), mean)
Work_Time_m <- rename(Work_Time_m,c("LOCATION"="Group.1","WorkTime_mean"="x"))
GDP_m <- aggregate(GDP[,3], list(GDP$LOCATION), mean)
GDP_m <- rename(GDP_m,c("LOCATION"="Group.1","GDP_mean"="x"))

tab0 <- left_join(Mental_Health_m, Income_Inequality_m, by = c("LOCATION"))
tab1 <- left_join(tab0, wages_m, by = c("LOCATION"))
tab2 <- left_join(tab1, Unemployment_m, by = c("LOCATION"))
tab3 <- left_join(tab2, Working_Age_m, by = c("LOCATION"))
tab4 <- left_join(tab3, Work_Time_m, by = c("LOCATION"))
tab5 <- left_join(tab4, GDP_m, by = c("LOCATION"))
tab_mean <- left_join(tab5, tab_countries, by=('LOCATION'))

kbl(tab_mean,caption = "**Table 1.b : List of OECD countries common for all our data's mean from 2000 to 2017 **: `tab_mean`") %>%
  kable_classic(full_width = T, html_font = "Cambria") %>%
  kable_styling(bootstrap_options = c('striped', 'hover', 'condensed'))
```


So now we have two tables with which we can perform our analysis and draw information for this first regression.

At this stage, we realized that for some of the countries we had selected (England, Hungary, Japan, Romania, Belgium, Brazil) the data was too insufficient to extract anything. Thus we will have to take this into account in our analysis in order not to bias our results.




----


## Question 2 : ???? Covid

For our second theme around Covid, we want to analyze if Covid-19 has had an impact on the population's mental-health.
We will consider several variables, in a selection of countries around the world: 

- antidepressant consumption (defined daily dosage per 1 000 inhabitants per day),
- unemployment rate (% of labour force),
- teleworking (Employed persons working from home as a % of the total employment). 

We found data on antidepressant consumption on the website : <https://www.oecd.org>, in the Pharmaceutical Market Section. 
Regarding the Covid data, they come from the site : <https://coronavirus.jhu.edu>. The `Cases` and `Deaths` variables we will use are cases and deaths - cumulative total per 100000 population.


Once again, we have made a selection of several countries which are the following : Austria, Belgium, Croatia, Czechia, Denmark, Finland, France, Germany, Greece, Hungary, Iceland, Ireland, Italy, Romania, Portugal, Poland, Norway, Netherlands, Switzerland, Sweden, Spain, Australia, Brazil, Canada, China, Japan, New-Zealand and the USA. 


```{r}
List.of.Countries = c('AUT','BEL','HRV', 'CZE', 'DNK', 'ENG', 'FIN', 'FRA', 'DEU', 'GRC', 'HUN','ISL',
                      'ITA', 'ROU', 'PRT', 'POL', 'NOR', 'NLD', 'CHE', 'SWE', 'ESP', 'AUS', 'BRA',
                      'CAN', 'CHN', 'JPN', 'NZL', 'USA')
```

For this first analysis related to the impact of Covid, R2.1, we quickly realized that the data available for antidepressant consumption in 2020 was very limited. We had to make a second selection of countries (`List.of.Countries2`) for this analysis in order to observe only the countries with data in 2020, during the covid year. 

```{r}
List.of.Countries2 = c('GRC', 'HUN', 'ISL', 'ITA', 'NOR','PRT', 'SWE', 'ESP')
```

Now we can select and sort the data. 
```{r}
Antidepressant_consumption <- read.csv(here::here("Data/Conso_Antidepressant.csv"))
attach(Antidepressant_consumption)
```

For all the variables we only kept the columns on the country, the date and the value of the variable, because they were the only ones that interested us. All the others have therefore been deleted.
It was also often necessary to rename the columns so that they all follow the scheme: LOCATION, TIME and VALUE.
Here is the table with data on antidepressant consumption between 2000 and 2020, for countries with data in 2020 (using the `List.of.Countries2`).

```{r}
Antidepressant_consumption <- Antidepressant_consumption[,-c(1:4,6:7,10:11)]
Antidepressant_consumption <- rename(Antidepressant_consumption,c("LOCATION"="COU","TIME"="Year","Antidepressant_Consumption"="Value"))
Antidepressant_consumption <- Antidepressant_consumption %>% filter(LOCATION %in% List.of.Countries)
Antidepressant_consumption2 <- Antidepressant_consumption %>% filter(LOCATION %in% List.of.Countries2)
```
```{r}
kbl(Antidepressant_consumption2[1:15,],caption = "**Table 2**^a^: `Antidepressant_consumption2` dataset") %>%
  kable_classic(full_width = T, html_font = "Cambria") %>%
  kable_styling(bootstrap_options = c('striped', 'hover', 'condensed'))%>%
  add_footnote(
      paste(
         "Representation of the first 15 observation of the dataset. Total observations : ",
         nrow(Antidepressant_consumption2)
      )
   )
```


We had to add a column with the date 2020 for the covid data, because it was not present, and rename columns in a simpler way.

```{r}
Number_Covid19_cases_deaths <- read.csv2(here::here("Data/CasesDeathsCovid.csv"))
attach(Number_Covid19_cases_deaths)
Number_Covid19_cases_deaths <- Number_Covid19_cases_deaths[-1,] 
Number_Covid19_cases_deaths <- Number_Covid19_cases_deaths[,-c(1:3,5:8,10:12)]
Number_Covid19_cases_deaths <- rename(Number_Covid19_cases_deaths, c("LOCATION"="Code","Cases"="Cases...cumulative.total.per.100000.population","Deaths"="Deaths...cumulative.total.per.100000.population"))
Number_Covid19_cases_deaths <- Number_Covid19_cases_deaths %>% add_column(TIME = 2020, .after = "LOCATION") 
Number_Covid19_cases_deaths$"Cases" <- as.numeric(Number_Covid19_cases_deaths$"Cases")
Number_Covid19_cases_deaths$"Deaths" <- as.numeric(Number_Covid19_cases_deaths$"Deaths")
Number_Covid19_cases_deaths <-  Number_Covid19_cases_deaths %>% filter(LOCATION %in% List.of.Countries)
Number_Covid19_cases_deaths2 <-  Number_Covid19_cases_deaths %>% filter(LOCATION %in% List.of.Countries2)

```

We can now form a table with all the data together, using the *full_join* function. 

```{r}
tab_R2.1 <- full_join(Number_Covid19_cases_deaths2, Antidepressant_consumption2, by= c("LOCATION","TIME"))
```

As the data of cases and death of the covid for the years before 2020 were displayed in NA, we assumed that its values were equal to 0. Also, the 'Cases' variable was output in character, we converted it to numeric.

```{r}
tab_R2.1[is.na(tab_R2.1)] <- 0 
tab_R2.1$Cases <- as.numeric(tab_R2.1$Cases)
```

```{r}
kbl(tab_R2.1[1:10,],caption = "**Table 2**^b^: `tab_R2.1`, Table of `Antidepressant_consumption2` and `Number_Covid19_cases_deaths2`") %>%
  kable_classic(full_width = T, html_font = "Cambria") %>%
  kable_styling(bootstrap_options = c('striped', 'hover', 'condensed'))%>%
  add_footnote(
      paste(
         "Representation of the first 10 observation of the dataset. Total observations : ",
         nrow(tab_R2.1)
      )
   )
```



Our table on the use of antidepressants and the number of cases and deaths of covid is now ready to be used. 

Given the little information we had on antidepressant consumption in 2020 (only for 8 countries) we decided to observe the rate of depression and finally include it in our research question.
We therefore wanted to analyze the evolution of the depression rate (prevalence of depressive disorders in % of the population) between 2010 and 2017, and if the covid had an impact on it in 2021. 
Our data comes from the sites : <https://ourworldindata.org/mental-health#depression> and <https://worldpopulationreview.com/>. 

```{r}
Depression_Rate2000_2017 <- read.csv(here::here("Data/Depression_Rate2000_2017.csv"))
attach(Depression_Rate2000_2017)
```

Here too we have only kept the country, the year and the value, and renamed the columns.As the years start before 2000, we have to make a selection of the years after 1999, to keep only what interests us. 

```{r}

Depression_Rate2000_2017 <- Depression_Rate2000_2017[-1]
Depression_Rate2000_2017 <- rename(Depression_Rate2000_2017,c("LOCATION"="Code","TIME"="Year","Depression_Rate"="Prevalence...Depressive.disorders...Sex..Both...Age..Age.standardized..Percent."))
Depression_Rate2000_2017 <- Depression_Rate2000_2017 %>% filter(LOCATION %in% List.of.Countries)
Depression_Rate2000_2017 <- Depression_Rate2000_2017 %>%
  filter(TIME>1999)
```

We did exactly the same thing for the depression rate in 2021. 
```{r}
Depression_Rate2021 <- read.csv2(here::here("Data/Depression_Rate2021.csv"))
attach(Depression_Rate2021)

Depression_Rate2021 <- Depression_Rate2021[,-c(1,3:4)]
Depression_Rate2021 <- rename(Depression_Rate2021,c("Depression_Rate"="prevalence"))
Depression_Rate2021 <- Depression_Rate2021 %>% filter(LOCATION %in% List.of.Countries)
Depression_Rate2021 <- Depression_Rate2021 %>% add_column(TIME = 2021, .after = "LOCATION") 
Depression_Rate2021$"Depression_Rate" <- as.numeric(Depression_Rate2021$"Depression_Rate")
```

Then, we had to join the two tables into one, using both *inner_join* and *pivot_longer* in order to obtain a table that we could use correctly afterwards to do analyses. 

```{r}
Depression_Rate2000_2021 <- Depression_Rate2000_2017 %>%
  rbind(Depression_Rate2021)%>%
  arrange(LOCATION,TIME)  
```

```{r}
kbl(Depression_Rate2000_2021[1:10,],caption = "**Table 2**^c^: `Depression_Rate2000_2021` dataset") %>%
  kable_classic(full_width = T, html_font = "Cambria") %>%
  kable_styling(bootstrap_options = c('striped', 'hover', 'condensed'))%>%
  add_footnote(
      paste(
         "Representation of the first 10 observation of the dataset. Total observations : ",
         nrow(Depression_Rate2000_2021)
      )
   )
```


For the second study of this theme, we want to see whether teleworking and unemployment rates can affect antidepressant use in selected countries. Information on Teleworking and Unemployment rate were extracted respectively from the sites : <https://ec.europa.eu/eurostat> and <https://data.oecd.org>. 

We will now use the data of antidepressant according to the first selected country list (`List.of.Countries`). 

As above, we have kept only the columns we were interested in, i.e. value, time and country, and we have renamed some inadequate columns. 

```{r}
Teleworking <- read.csv2(here::here("Data/Teleworking.csv"))
attach(Teleworking)
Teleworking <- Teleworking[,-c(1:8,12)]
Teleworking <- rename(Teleworking,c("LOCATION"="geo","TIME"="TIME_PERIOD","Teleworking"="OBS_VALUE"))
Teleworking <-  Teleworking %>% filter(LOCATION %in% List.of.Countries)
```
```{r}
kbl(Teleworking[1:10,],caption = "**Table 2**^d^: `Teleworking` dataset") %>%
  kable_classic(full_width = T, html_font = "Cambria") %>%
  kable_styling(bootstrap_options = c('striped', 'hover', 'condensed'))%>%
  add_footnote(
      paste(
         "Representation of the first 10 observation of the dataset. Total observations : ",
         nrow(Teleworking)
      )
   )
```

We also did this for the unemployment rate. 

```{r}
UnemploymentCovid <- read.csv(here::here("Data/Unemployement_Rate2.csv"))
attach(UnemploymentCovid)
UnemploymentCovid <- UnemploymentCovid[,-c(2:5,8)]
UnemploymentCovid <- rename(UnemploymentCovid, c("Unemployment"="Value"))
UnemploymentCovid <-  UnemploymentCovid %>% filter(LOCATION %in% List.of.Countries)
```
```{r}
kbl(UnemploymentCovid[1:10,],caption = "**Table 2**^e^: `UnemploymentCovid` dataset, Unemployment rate from 2000 to 2020 (covid year)") %>%
  kable_classic(full_width = T, html_font = "Cambria") %>%
  kable_styling(bootstrap_options = c('striped', 'hover', 'condensed'))%>%
  add_footnote(
      paste(
         "Representation of the first 10 observation of the dataset. Total observations : ",
         nrow(UnemploymentCovid)
      )
   )
```

With the *full_join* function we have gathered the data of these three variables in a single table.
For the good functioning of the table for further analysis, it was necessary to remove the NA values, and to convert the variable "teleworking" in numerical (which was in character). 

```{r}
Data <- left_join(Antidepressant_consumption, Teleworking, by=c("LOCATION", "TIME"))
tab_R2.2 <- left_join(Data, UnemploymentCovid, by = c("LOCATION", "TIME"))
tab_R2.2$Teleworking <- as.numeric(tab_R2.2$Teleworking)

kbl(tab_R2.2[1:20,],caption = "**Table 2**^f^: `tab_R2.2`, Table of `Antidepressant_consumption`, `Teleworking` and `UnemploymentCovid`") %>%
  kable_classic(full_width = T, html_font = "Cambria") %>%
  kable_styling(bootstrap_options = c('striped', 'hover', 'condensed'))%>%
  add_footnote(
      paste(
         "Representation of the first 10 observation of the dataset. Total observations : ",
         nrow(tab_R2.2)
      )
   )
```

We now have three tables ready to be used and analyzed in the next parts: 
- *tab_R2.1* with antidepressants consumption for countries where we have data on this consumption in 2020, and Covid Cases and deaths
- *Depression_Rate2000_2021* table 
- *tab_R2.2* with antidepressants consumption, teleworking, and the unemployment rate. 

----

## Question 3 : ??? Public spendings on health 


In this thrid analysis of datasets,  we are going to compare the prevalence of mental health disorder (% of the population (age-standardaized)) in a population of a country and the current health expenditure (% of GDP). Particularly focus on the countries of the OCDE that is The Organisation for Economic Co-operation and Development.

The sources of our datas comes from the website : <https://data.worldbank.org/indicator/SH.XPD.CHEX.GD.ZS> for the current health expenditure in the countries and <https://ourworldindata.org/mental-health> for the Mental health datas.

Our intitial question of research is: 

- Can health care systems such as financial investments in overall health, access to medication explain and predict cross-country differences in mental disorders in the population? Is a country that invests more in public health for its population the country where there is less mental illness?

- Our influenced variable Y is therefore the prevalence of mental health disorder (% of the population)
- our independant variable X is the current health expenditure (% of the GDP)
- The access to medication is a difficulte variable to quantify, we did not find data corresponding to that. Therefore, our analysis is focus on these two variables X and Y. 


### List.of.countries

In continuation of our analysis, we keep the OECD countries to answer our research question.

```{r}
tab.of.countries <- read.csv2(here::here('Data/Entities_LOCATION_Region.csv'))
```


### 1: Cleaning Public spending on health

Importation of the dataset Public.spending on health. This dataframe represent Current health expenditure (% of GDP) of each countries.

```{r}
Public.spending.on.health_New <- read.csv2(here::here('Data/Public.spending.on.health.csv'))
```
                                       
This dataset of Public sprending on health has a bad structure initially.
We remove the 3 first rows and we rename the different variables in the columns to get the same structure as previously.

```{r}
Public.spending.on.health_New <- Public.spending.on.health_New[-c(1:3),]

Public.spending.on.health_New <- rename(Public.spending.on.health_New, c('Country' = 'Data.Source', 'LOCATION' = 'World.Development.Indicators'))
```

Then we need to remove the unecessary columns, with no data corresponding, which means the missing values from 1960 to 1999 and from 2019-2020. Deleting this columns will not biais our analysis because there are NA for every observations. We believe that the data about the public health expenditures started to be recorded in 2000.

Also, the 'Indicator Name', 'Indicator Code' are unrelevant datas.

```{r}
Public.spending.on.health_New <- Public.spending.on.health_New[,-c(5:44)]
Public.spending.on.health_New$X.61 <- NULL
Public.spending.on.health_New$Country <- NULL
Public.spending.on.health_New$X <- NULL
Public.spending.on.health_New$X.1 <- NULL
Public.spending.on.health_New$X.62 <- NULL
Public.spending.on.health_New$X.63 <- NULL
```

 Our initial dataframe as for variables names [(X.n),(X.n+1)...(X.m)], we need to transform them as Years, 'Time':[2000,2001...2018]. 

```{r}
Public.spending.on.health_New <- rename(Public.spending.on.health_New, c('2000'='X.42','2001'='X.43','2002'='X.44','2003'='X.45', '2004'='X.46','2005'='X.47','2006'='X.48','2007'='X.49', '2008'='X.50','2009'='X.51','2010'='X.52', '2011'='X.53','2012'='X.54','2013'='X.55','2014'='X.56','2015'='X.57','2016'='X.58','2017'='X.59','2018'='X.60'))

Public.spending.on.health_New <- Public.spending.on.health_New[-1,]
```

Then, we use **pivot_longer** to attribute each value (Value_Spending.on.health) to the corresponding 'Time' (the year) and 'LOCATION'(the code of the country). This will transform our dataframe with the years in rows and not in columns.

```{r}
Public.spending.on.health_New <- Public.spending.on.health_New %>% 
  pivot_longer(cols = c('2000','2001','2002','2003','2004','2005','2006','2007','2008','2009','2010','2011','2012','2013','2014','2015','2016','2017','2018'),names_to = 'Time', values_to = 'Value_Spending.on.health')
```

Finally we have a new dataframe of the Current health expenditure (% of GDP) of each countries attributed to the Time (from 2000 to 2018).


#### 2: Cleaning Mental Health

Now we import the  share with mental and substance disorders data corresponding to a list of countries. Our goal is to compare the prevalence of mental health disorder in a population of a country with respect to the public investments on health.

```{r}
share.with.mental.and.substance.disorders <- read.csv2(here::here('Data/share-with-mental-and-substance-disorders.csv'))
```
This dataset has already a good structure, the same as the others for our analysis. The value Y; 'prevalence mental and substance use disorders.sex.both.age stanrdaized percent', represents more clearly the proportion of the population in % sufuring from mental illness in a given country. 

We rename our (share.with.mental.and.substance.disorders) dataframe into Mental_Health.

```{r}
Mental_Health <- share.with.mental.and.substance.disorders                                                       
```

We remove the 'Entity' column. Indeed we refer only to the 'LOCATION' as code.
```{r}
Mental_Health <- Mental_Health[,-1]
```

We rename the variable column of year with 'Time', the Code with 'LOCATION' and
Prevalence...Mental.and.substance.use.disorders...Sex..Both...Age..Age.standardized..Percent. with 'Mental_health_value'.

```{r}
Mental_Health <- Mental_Health %>%
  rename(Time=Year)

Mental_Health <- Mental_Health %>%
  rename(LOCATION=Code)

Mental_Health1 <- rename(Mental_Health, 'Mental_health_Value' = 'Prevalence...Mental.and.substance.use.disorders...Sex..Both...Age..Age.standardized..Percent.')
```

After this, we want to filter the data with the value going from 2000 to 2017. Why do we keep only these values?
Because we consider it as a relevant horizon of time and we will need to fit these values to the public spendinds on health for our final table. So we must keep the same strucure.

```{r}
Mental_Health <- Mental_Health1 %>%
  group_by(LOCATION,Mental_health_Value) %>%
  filter(Time>1999)
```

Our analysis is focus on a specific list of countries. We consider it relevant to take a sample of 28 countries with different structural characteristics. 
Here is the following selected countries: 'AUT','BEL','HRV', 'CZE', 'DNK', 'ENG', 'FIN', 'FRA','UK','DEU', 'GRC', 'HUN', 'ISL', 'ITA', 'ROU', 'PRT', 'POL', 'NOR', 'NLD', 'CHE', 'SWE', 'ESP', 'AUS', 'BRA', 'CAN', 'CHN', 'JPN', 'NZL', 'USA'

The countries in this list our part of the OCDE. We make this selection because taking all the countries is the world would result to:
- Too many observations 
- Extreme values
- Unrelevant to the research question 

```{r}
List.of.Countries = c('AUT','BEL','HRV', 'CZE', 'DNK', 'ENG', 'FIN', 'FRA', 'UK','DEU', 'GRC', 'HUN', 'ISL', 'ITA', 'ROU', 'PRT', 'POL', 'NOR', 'NLD', 'CHE', 'SWE', 'ESP', 'AUS', 'BRA', 'CAN', 'CHN', 'JPN', 'NZL', 'USA')

Mental_Health_2 <-  Mental_Health %>%
  filter(LOCATION %in% List.of.Countries)

Public.spending.on.health_New_2 <- Public.spending.on.health_New %>% 
  filter(LOCATION %in% List.of.Countries)
```
----


### 3: Merge the datasets

We merge the two dataframes into one single table named tab_1. We join them by 'LOCATION' and 'Time'. Moreover, we add the 'Region' and the 'Entity' from the table: 'list.of.countries'

```{r}
tab_1 <- merge(Public.spending.on.health_New_2, Mental_Health_2, by = c('LOCATION', 'Time'))
tab_1 <- merge(tab_1, tab.of.countries, by=('LOCATION'))
```

We need the values as numeric and not as characters for the analysis. We characterise the Regions and Locations into factors for our future analysis.

```{r}
Mental_Health_2 <-  merge(Mental_Health_2,tab.of.countries, by='LOCATION')
Public.spending.on.health_New_2 <- merge(Public.spending.on.health_New_2, tab.of.countries, by='LOCATION')

Public.spending.on.health_New_2$Value_Spending.on.health <- as.numeric(Public.spending.on.health_New_2$Value_Spending.on.health)
Mental_Health_2$Mental_health_Value <- as.numeric(Mental_Health_2$Mental_health_Value)
```

```{r}
tab_1$Value_Spending.on.health <- as.numeric(tab_1$Value_Spending.on.health)
tab_1$Mental_health_Value <- as.numeric(tab_1$Mental_health_Value)
tab_1$Time <- as.numeric(tab_1$Time)
tab_1$LOCATION <- as.factor(tab_1$LOCATION)
tab_1$Region <- as.factor(tab_1$Region)
tab_1 <- tab_1[c(1,5,6,2,3,4)]
```

Now our final table, tab_1, is arranged in the structure that will be used to make the analysis.

```{r}
kbl(tab_1[1:20,],caption = "*Table of Public spending on health and mental health**: `tab_1`, ...") %>%
  kable_classic(full_width = T, html_font = "Cambria") %>%
  kable_styling(bootstrap_options = c('striped', 'hover', 'condensed'))
```

For further analysis, for instance cluster analysis, we decide to sort the dataset (tab_1) with the aggregated values.

```{r}
tab_Mean_Value_Spending.on.health <- aggregate(tab_1$Value_Spending.on.health, list(tab_1$LOCATION,tab_1$Entity,tab_1$Region), mean)

tab_Mean_Value_Spending.on.health <- rename(tab_Mean_Value_Spending.on.health,c("LOCATION"="Group.1","Entity"="Group.2","Region"="Group.3","Mean_Value_Spending.on.health"="x"))
```

Aggregate the Mental_health_Value
```{r}
tab_Mean_Mental_health_Value <- aggregate(tab_1$Mental_health_Value, list(tab_1$LOCATION,tab_1$Entity,tab_1$Region), mean)

tab_Mean_Mental_health_Value <- rename(tab_Mean_Mental_health_Value,c("LOCATION"="Group.1","Entity"="Group.2","Region"="Group.3", "Mean_Mental_health_Value"="x"))
```

We merge the table into a new dataframe representing the mean values with respect to the countries and Region into: tab_2

```{r}
tab_2 <- merge(tab_Mean_Value_Spending.on.health, tab_Mean_Mental_health_Value, by = c('LOCATION','Entity','Region'))
```

```{r}
kbl(tab_2[1:20,],caption = "*Table aggregated of Public spending on health and mental health**: `tab_2`, ...") %>%
  kable_classic(full_width = T, html_font = "Cambria") %>%
  kable_styling(bootstrap_options = c('striped', 'hover', 'condensed'))
```




