---
title: "Data"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE) # supprimer ? a quoi il sert ?
```

```{r, echo=FALSE, message=FALSE}
#faire un code qui ouvre tous les packages dans un autre file (--> setup.R)

```

For our research, we are going to use different datasets for our three main themes. 

## Work Environment

First of all, for the database concerning the environment at work, we have extracted all the data from
the sites : <https://www.oecd.org> and <https://ourworldindata.org>. 

We have chosen the information of 7 variables, for a selection of countries, and for a period from
2000 to 2017. 

```{r}
#creer un code pour ouvrir les données depuis le bonne endroit, car il y aura un doc avec toutes les
#données en csv. 
```

````{r}
#mettre les codes pour trier toutes les donnees et avoir un seul tableau et decrire ce qu'on fait 
````

## Covid 

For our second theme around Covid, we found data on antidepressant consumption on the website : 
<https://www.oecd.org>, in the Pharmaceutical Market Section. 
Regarding the Covid data, they come from the site : <https://coronavirus.jhu.edu>. Finally, 
informations on Teleworking and Unemployement were extracted respectively from the sites : 
<https://ec.europa.eu/eurostat> and <https://data.oecd.org>. 










