---
title: "Data"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE) # supprimer ? a quoi il sert ?
```

First, we need to install different packages. 

```{r, echo=FALSE, message=FALSE}
library(plyr)
library(dbplyr)
library(tidyverse)
library(tibble)
library(corrplot)
library(car)
#faire un code qui ouvre tous les packages dans un autre file (--> setup.R)
```

For our research, we are going to use different datasets for our three main themes. 

## Work Environment

First of all, for the database concerning the environment at work, we have extracted all the data from the sites : <https://www.oecd.org> and <https://ourworldindata.org>. 

We have chosen the information of 7 variables, for a selection of countries, and for a period from 2000 to 2017. 

```{r}
#creer un code pour ouvrir les données depuis le bonne endroit, car il y aura un doc avec toutes les
#données en csv. 
```

````{r}
#mettre les codes pour trier toutes les donnees et avoir un seul tableau et decrire ce qu'on fait 
````

## Covid 

For our second theme around Covid, we wanted to analyze if Covid had an impact on antidepressant consumption and we found data on antidepressant consumption on the 
website : <https://www.oecd.org>, in the Pharmaceutical Market Section. 
Regarding the Covid data, they come from the site : <https://coronavirus.jhu.edu>. 

First of all, we have made a selection of several countries which are the following (To simplify, country codes have been used and not the full names) : Austria, 
Belgium, Croatia, Czechia, Denmark, Finland, France, Germany, Greece, Hungary, Iceland, Ireland, Italy, Romania, Portugal, Poland, Norway, Netherlands, Switzerland, 
Sweden, Spain, Australia, Brazil, Canada, China, Japan, New-Zealand and the USA.  

```{r}
List.of.Countries = c('AUT','BEL','HRV', 'CZE', 'DNK', 'ENG', 'FIN', 'FRA', 'DEU', 'GRC', 'HUN','ISL','ITA', 'ROU', 'PRT', 'POL', 'NOR', 'NLD', 'CHE',
'SWE','ESP','AUS', 'BRA','CAN', 'CHN', 'JPN', 'NZL', 'USA')
```

Now we can select and sort the data. 

```{r}
Antidepressant_consumption <- read.csv("Conso Antidepressant.csv") #--> Mettre un code qui sélectionne la donnée depuis le bon emplacement : read.csv(here::here("data/Conso Antidepressant.csv")) ? 
attach(Antidepressant_consumption)
Antidepressant_consumption <- Antidepressant_consumption[,-c(1:4,6:7,10:11)]
Antidepressant_consumption <- rename(Antidepressant_consumption,c("LOCATION"="COU","TIME"="Year"))
Antidepressant_consumption1 <- Antidepressant_consumption %>% filter(LOCATION %in% List.of.Countries2)
View(Antidepressant_consumption1)
````









