---
title: "Data"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE) # supprimer ? a quoi il sert ?
```
For our research, we are going to use different datasets for our three main themes. 

First, we need to install different packages. 

```{r, echo=FALSE, message=FALSE}
library(plyr)
library(dbplyr)
library(tidyverse)
library(tibble)
library(corrplot)
library(car)
#faire un code qui ouvre tous les packages dans un autre file (--> setup.R)
```

## Work Environment

First of all, for the database concerning the environment at work, we have extracted all the data from the sites : <https://www.oecd.org> and <https://ourworldindata.org>. 

Our first resarch question was : Given the structure of the working environment in different countries, can we say that the mental health of the population is influenced by the working conditions and the situation of the country?

To see those effects, we have chosen the information of 6 independants variables ; 

- the average work-time
- the GPD
- the unemployment rate 
- the working age population
- the salaries
- the income inequalities 

 --> Regression 1 : MentalHealth = x1*IncomeInequality + x2*wages + x3*Unemployment + x4*WorkingAgePopulation + x5*WorkTime + x6*GPD

We have made a selection of several countries which are the following (To simplify, country codes have been used and not the full names) : Austria, Belgium, Croatia, Czechia, Denmark, Finland, France, Germany, Greece, Hungary, Iceland, Ireland, Italy, Romania, Portugal, Poland, Norway, Netherlands, Switzerland, Sweden, Spain, Australia, Brazil, Canada, Japan, New-Zealand and the USA.  

```{r}
List.of.Countries = c('AUT','BEL','HRV', 'CZE', 'DNK', 'ENG', 'FIN', 'FRA', 'DEU', 'GRC', 'HUN', 'ISL', 'ITA', 'ROU', 'PRT', 'POL', 'NOR', 'NLD', 'CHE', 'SWE', 'ESP', 'AUS', 'BRA', 'CAN', 'JPN', 'NZL', 'USA')
```

Now that we have collected all our data, we need to sort, order and rename them in order to obtain only tables with three columns to have the value of our variable according to its country and its date. We took the data for each of these variables for a certain sample of countries and then chose to do an individual average over the years from 2000 to 2017.

```{r}
ental_Health <- read.csv("Mental Health.csv")
attach(Mental_Health)
Mental_Health <- Mental_Health[,-1]
Mental_Health <- rename(Mental_Health,c("LOCATION"="Code", "TIME"="Year","ValueH"="Prevalence...Mental.and.substance.use.disorders...Sex..Both...Age..Age.standardized..Percent."))
Mental_Health <-  Mental_Health %>% filter(LOCATION %in% List.of.Countries)
Mental_Health <- Mental_Health %>%
  filter(TIME>1999, TIME< 2018)
Mental_Health_m <- aggregate(Mental_Health[,3], list(Mental_Health$LOCATION), mean)
Mental_Health_m <- rename(Mental_Health_m,c("LOCATION"="Group.1","Mean_1"="x"))

Income_Inequality <- read.csv2("Income inequality-1.csv")
attach(Income_Inequality)
Income_Inequality <- Income_Inequality[,-c(2:5,8)]
Income_Inequality$Value <- as.numeric(Income_Inequality$Value)
Income_Inequality <-  Income_Inequality %>% filter(LOCATION %in% List.of.Countries)
Income_Inequality <- Income_Inequality %>%
  filter(TIME>1999, TIME< 2018)
Income_Inequality_m <- aggregate(Income_Inequality[,3], list(Income_Inequality$LOCATION), mean)
Income_Inequality_m <- rename(Income_Inequality_m,c("LOCATION"="Group.1","Mean_2"="x"))

wages <- read.csv("Average wages.csv")
attach(wages)
wages <- wages[,-c(2:5,8)]
wages <-  wages %>% filter(LOCATION %in% List.of.Countries)
wages <- wages %>%
  filter(TIME>1999, TIME< 2018)
wages_m <- aggregate(wages[,3], list(wages$LOCATION), mean)
wages_m <- rename(wages_m,c("LOCATION"="Group.1","Mean_3"="x"))

Unemployment <- read.csv("Unemployement Rate.csv")
attach(Unemployment)
Unemployment <- Unemployment[,-c(2:5,8)]
Unemployment <-  Unemployment %>% filter(LOCATION %in% List.of.Countries)
Unemployment <- Unemployment %>%
  filter(TIME>1999, TIME< 2018)
Unemployment_m <- aggregate(Unemployment[,3], list(Unemployment$LOCATION), mean)
Unemployment_m <- rename(Unemployment_m,c("LOCATION"="Group.1","Mean_4"="x"))

Working_Age <- read.csv("Working age population.csv")
attach(Working_Age)
Working_Age <- Working_Age[,-c(2:5,8)]
Working_Age <-  Working_Age %>% filter(LOCATION %in% List.of.Countries)
Working_Age_m <- aggregate(Working_Age[,3], list(Working_Age$LOCATION), mean)
Working_Age_m <- rename(Working_Age_m,c("LOCATION"="Group.1","Mean_5"="x"))

Work_Time <- read.csv("Avg Work Time.csv")
attach(Work_Time)
Work_Time <- Work_Time[,-c(2:5,8)]
Work_Time <-  Work_Time %>% filter(LOCATION %in% List.of.Countries)
Work_Time <- Work_Time %>%
  filter(TIME>1999, TIME< 2018)
Work_Time_m <- aggregate(Work_Time[,3], list(Work_Time$LOCATION), mean)
Work_Time_m <- rename(Work_Time_m,c("LOCATION"="Group.1","Mean_6"="x"))

GDP <- read.csv("gdp-per-capita.csv")
attach(GDP)
GDP <- GDP[,-c(1,5)]
GDP <- rename(GDP,c("LOCATION"="Code", "TIME"="Year"))
GDP <-  GDP %>% filter(LOCATION %in% List.of.Countries)
GDP <- GDP %>%
  filter(TIME>1999, TIME< 2018)
GDP_m <- aggregate(GDP[,3], list(GDP$LOCATION), mean)
GDP_m <- rename(GDP_m,c("LOCATION"="Group.1","Mean_7"="x"))
```

Now that we have all our variables in the right format, we need to put them in a common table so that we can have an overall representation and be able to observe and analyze the trends that emerge.

```{r}
tab_0 <- full_join(Mental_Health_m, Income_Inequality_m, by = c("LOCATION"))
tab_1 <- full_join(tab_0, wages_m, by = c("LOCATION"))
tab_2 <- full_join(tab_1, Unemployment_m, by = c("LOCATION"))
tab_3 <- full_join(tab_2, Working_Age_m, by = c("LOCATION"))
tab_4 <- full_join(tab_3, Work_Time_m, by = c("LOCATION"))
tab_R1 <- full_join(tab_4, GDP_m, by = c("LOCATION"))
tab_R1 <- na.omit(tab_R1)
tab_R1 <- rename(tab_R1, c("Mental_Health"="Mean_1","Income_Inequality"="Mean_2","wages"="Mean_3","Unemployment"="Mean_4","Working_Age"="Mean_5","Work_Time"="Mean_6","GDP"="Mean_7"))
```
Because of the large amount of data we used, some countries were left out due to lack of information, which made them insufficient to compare with others.

As our linear relationship doesn't seem satisfying, we decide to flatten our values and obtain more meaningful results, we converted our table using the log function. 

````{r}
tab_R1_log <- log(tab_R1[,2:8])
tab_Tot <- cbind(tab_R1$LOCATION, tab_R1_log)
tab_Tot <- rename(tab_Tot, c("LOCATION"="tab_R1$LOCATION"))
View(tab_Tot)
plot(tab_Tot)
```

"Anxiety" and "Depression" are two of the major determinants of our mental health variable. Our next objective is therefore to analyze whether one or the other would have a significant impact on the work environment.

````{r}
Anxiety <- read.csv("share-with-anxiety-disorders.csv")
attach(Anxiety)
Anxiety <- Anxiety[,-1]
Anxiety <- rename(Anxiety ,c("LOCATION"="Code", "TIME"="Year"))
Anxiety <-  Anxiety %>% filter(LOCATION %in% List.of.Countries)
Anxiety <- Anxiety %>%
  filter(TIME>1999, TIME< 2018)
Anxiety_m <- aggregate(Anxiety[,3], list(Anxiety$LOCATION), mean)
Anxiety_m <- rename(Anxiety_m,c("LOCATION"="Group.1","Mean_1"="x"))

Depression <- read.csv("dalys-depression-age-std-rate.csv")
attach(Depression)
Depression <- Depression[,-1]
Depression <- rename(Depression ,c("LOCATION"="Code", "TIME"="Year"))
Depression <-  Depression %>% filter(LOCATION %in% List.of.Countries)
Depression <- Depression %>%
  filter(TIME>1999, TIME< 2018)
Depression_m <- aggregate(Depression[,3], list(Depression$LOCATION), mean)
Depression_m <- rename(Depression_m,c("LOCATION"="Group.1","Mean_1"="x"))
```





## Covid

For our second theme around Covid, we want to analyze if Covid had an impact on antidepressant 
consumption in selected countries around the world. We found data on antidepressant consumption on the website : <https://www.oecd.org>, in the Pharmaceutical Market Section. 
Regarding the Covid data, they come from the site : <https://coronavirus.jhu.edu>. 

Regression 2.1 : Antidepressant_consumption = a*Number_Covid-19_cases + b*Number_Covid-19_Death

Once again, we have made a selection of several countries which are the following : Austria, Belgium, Croatia, Czechia, Denmark, Finland, France, Germany, Greece, Hungary, Iceland, Ireland, Italy, Romania, Portugal, Poland, Norway, Netherlands, Switzerland, Sweden, Spain, Australia, Brazil, Canada, China, Japan, New-Zealand and the USA.  

```{r}
List.of.Countries = c('AUT','BEL','HRV', 'CZE', 'DNK', 'ENG', 'FIN', 'FRA', 'DEU', 'GRC', 'HUN','ISL',
                      'ITA', 'ROU', 'PRT', 'POL', 'NOR', 'NLD', 'CHE', 'SWE', 'ESP', 'AUS', 'BRA',
                      'CAN', 'CHN', 'JPN', 'NZL', 'USA')
```

For this first analysis related to the impact of Covid, R2.1, we quickly realized that the data available for antidepressant consumption in 2020 was very limited. We had to make a second selection of countries for this regression in order to observe only the countries with data in 2020, during the covid year. 

```{r}
List.of.Countries2 = c('GRC', 'HUN', 'ISL', 'ITA', 'NOR','PRT', 'SWE', 'ESP')
```

Now we can select and sort the data. 
```{r}
Antidepressant_consumption <- read.csv("Conso Antidepressant.csv") #--> Mettre un code qui sélectionne la donnée depuis le bon emplacement : read.csv(here::here("data/Conso Antidepressant.csv")) ? 
attach(Antidepressant_consumption)
```

For all the variables we only kept the columns on the country, the date and the value of the variable, because they were the only ones that interested us. All the others have therefore been deleted.
It was also often necessary to rename the columns so that they all follow the scheme: LOCATION, TIME and VALUE. 

```{r}
Antidepressant_consumption <- Antidepressant_consumption[,-c(1:4,6:7,10:11)]
Antidepressant_consumption <- rename(Antidepressant_consumption,c("LOCATION"="COU","TIME"="Year"))
Antidepressant_consumption <- Antidepressant_consumption %>% filter(LOCATION %in% List.of.Countries)
Antidepressant_consumption1 <- Antidepressant_consumption %>% filter(LOCATION %in% List.of.Countries2)
View(Antidepressant_consumption)
```

We had to add a column with the date 2020 for the covid data, because it was not present. 
```{r}
Number_Covid19_cases_deaths <- read.csv2("Cases + Deaths Covid.csv")
attach(Number_Covid19_cases_deaths)
Number_Covid19_cases_deaths <- Number_Covid19_cases_deaths[,-c(1,2,4:7,9:12)]
Number_Covid19_cases_deaths <- Number_Covid19_cases_deaths[-1,] 
Number_Covid19_cases_deaths <- rename(Number_Covid19_cases_deaths, "LOCATION"="Code")
Number_Covid19_cases_deaths <- Number_Covid19_cases_deaths %>% add_column(TIME = 2020, .after = "LOCATION") 
Number_Covid19_cases_deaths <-  Number_Covid19_cases_deaths %>% filter(LOCATION %in% List.of.Countries)
Number_Covid19_cases_deaths1 <-  Number_Covid19_cases_deaths %>% filter(LOCATION %in% List.of.Countries2)
View(Number_Covid19_cases_deaths)
```

We can now form a table with all the data together, using the *full_join* function. 

```{r}
tab_R2.1 <- full_join(Number_Covid19_cases_deaths1, Antidepressant_consumption1, by= c("LOCATION","TIME"))
```

As the data of cases and death of the covid for the years before 2020 were displayed in NA, we assumed that its values were equal to 0. Also, the "cases" variable was output in character, we converted it to numeric.

```{r}
tab_R2.1[is.na(tab_R2.1)] <- 0 
tab_R2.1$Cases...cumulative.total <- as.numeric(tab_R2.1$Cases...cumulative.total)
View(tab_R2.1)
```
Our table on the use of antidepressants and the number of cases and deaths of covid is now ready to be used. 

Given the little information we had on antidepressant consumption in 2020 (only for 8 countries) we decided to observe the rate of depression and finally include it in our research question.
We therefore wanted to analyze the evolution of the depression rate between 2010 and 2017, and if the covid had an impact on it in 2021. Our data comes from the sites : <https://ourworldindata.org/mental-health#depression> and <https://worldpopulationreview.com/>. 

```{r}
Depression_Rate2000_2017 <- read.csv("Depression Rate 2000:2017.csv")
attach(Depression_Rate2000_2017)
View(Depression_Rate2000_2017)
```

Here too we have only kept the country, the year and the value, and renamed the columns.As the years start before 2000, we have to make a selection of the years after 1999, to keep only what interests us. 

```{r}
Depression_Rate2000_2017 <- Depression_Rate2000_2017[-1]
Depression_Rate2000_2017 <- rename(Depression_Rate2000_2017,c("LOCATION"="Code","TIME"="Year","Value"="Prevalence...Depressive.disorders...Sex..Both...Age..Age.standardized..Percent."))
Depression_Rate2000_2017 <- Depression_Rate2000_2017 %>% filter(LOCATION %in% List.of.Countries)
Depression_Rate2000_2017 <- Depression_Rate2000_2017 %>%
  filter(TIME>1999)
Depression_Rate2017 <- Depression_Rate2000_2017 %>%
  filter(TIME>2016)
Depression_Rate2017 <- rename(Depression_Rate2017,c("2017"="Value"))
Depression_Rate2017 <- Depression_Rate2017[-2]
View(Depression_Rate2017)
```

We did exactly the same thing for the depression rate in 2021. 
```{r}
Depression_Rate2021 <- read.csv2("Depression Rate 2021.csv")
attach(Depression_Rate2021)
Depression_Rate2021 <- Depression_Rate2021[,-c(1,3:4)]
Depression_Rate2021 <- rename(Depression_Rate2021,c("2021"="prevalence"))
Depression_Rate2021 <- Depression_Rate2021 %>% filter(LOCATION %in% List.of.Countries)
Depression_Rate2021 <- Depression_Rate2021 %>% add_column(TIME = 2021, .after = "LOCATION") 
Depression_Rate2021 <- Depression_Rate2021[-3]
View(Depression_Rate2021)
```

Then, we had to join the two tables into one, using both *inner_join* and *pivot_longer* in order to obtain a table that we could use correctly afterwards to do analyses. 

```{r}
tab_R2.1.1 <- Depression_Rate2017 %>%
  inner_join(Depression_Rate2021, by = "LOCATION")
tab_R2.1.1$"2021" <- as.numeric(tab_R2.1.1$"2021")
tab_R2.1.1 <- tab_R2.1.1 %>%
  pivot_longer(c(`2017`, `2021`),
               names_to = "TIME",
               values_to = "VALUE")
View(tab_R2.1.1)
```

For the second study of this theme, we want to see whether teleworking and unemployment rates can affect antidepressant use in selected countries. Information on Teleworking and Unemployment rate were extracted respectively from the sites : <https://ec.europa.eu/eurostat> and <https://data.oecd.org>. 

We will now use the data of antidepressant according to the first selected country list. 
```{r}
View(Antidepressant_consumption)
```

As above, we have kept only the columns we were interested in, i.e. value, date and country, and we have renamed some inadequate columns. 

```{r}
Teleworking <- read.csv2("Teleworking.csv")
attach(Teleworking)
Teleworking <- Teleworking[,-c(1:8,12)]
Teleworking <- rename(Teleworking,c("LOCATION"="geo","TIME"="TIME_PERIOD","Teleworking"="OBS_VALUE"))
Teleworking <-  Teleworking %>% filter(LOCATION %in% List.of.Countries)
View(Teleworking)
```

We also did this for the unemployment rate. 

```{r}
UnemploymentCovid <- read.csv("Unemployement Rate.csv")
attach(UnemploymentCovid)
UnemploymentCovid <- UnemploymentCovid[,-c(2:5,8)]
UnemploymentCovid <- rename(UnemploymentCovid, c("Unemployment"="Value"))
UnemploymentCovid <-  UnemploymentCovid %>% filter(LOCATION %in% List.of.Countries)
View(UnemploymentCovid)
```

With the *full_join* function we have gathered the data of these three variables in a single table.
For the good functioning of the table for further analysis, it was necessary to remove the NA values, and to convert the variable "teleworking" in numerical (which was in character). 

```{r}
tab <- full_join(Antidepressant_consumption, Teleworking, by=c("LOCATION", "TIME"))
tab_R2.2 <- full_join(tab, UnemploymentCovid, by = c("LOCATION", "TIME"))
tab_R2.2 <- na.omit(tab_R2.2)
tab_R2.2$Teleworking <- as.numeric(tab_R2.2$Teleworking)
View(tab_R2.2)
```





## Public spendings on health 



In this thrid analysis of datasets,  we are going to compare the prevalence of mental health disorder (in % of the population (age-standardaized)) in a population of a country and the current health expenditure (% of GDP).

The sources of our datas comes from the website : <https://data.worldbank.org/indicator/SH.XPD.CHEX.GD.ZS> for the current health expenditure in the countries and <https://ourworldindata.org/mental-health> for the Mental health datas.

Our intitial question of research is: 
- Can health care systems such as financial investments in overall health, access to medication explain and predict cross-country differences in mental disorders in the population? Is a country that invests more in public health for its population the country where there is less mental illness?

- Our influenced variable Y is therefore the prevalence of mental health disorder 
- our independant variable X is the current health expenditure


Importation of the data set Public.spending on health. This dataframe represent Current health expenditure (% of GDP) of each countries.

```{r}
Public.spending.on.health <- read.csv2(here::here('data/Regression_3/Public.spending.on.health.csv'))
```
                                       
We remove the 3 first rows and we rename the different variables in the columns.

```{r}
Public.spending.on.health_New <- Public.spending.on.health_New[-c(1:3),]

Public.spending.on.health_New <- rename(Public.spending.on.health_New, c('Country' = 'Data.Source', 'LOCATION' = 'World.Development.Indicators'))
```

We remove the unecessary columns, with no data corresponding and we remove the unecessary columns with no relevant data.

```{r}
Public.spending.on.health_New <- Public.spending.on.health_New[,-c(5:44)]
Public.spending.on.health_New$X.61 <- NULL
Public.spending.on.health_New$Country <- NULL
Public.spending.on.health_New$X <- NULL
Public.spending.on.health_New$X.1 <- NULL
Public.spending.on.health_New$X.62 <- NULL
Public.spending.on.health_New$X.63 <- NULL
```

 Our initial dataframe as for variables [(X.n),(X.n+1)...(X.m)], we need to transform them as Years. 

```{r}
Public.spending.on.health_New <- rename(Public.spending.on.health_New, c('2000'='X.42','2001'='X.43','2002'='X.44','2003'='X.45', '2004'='X.46','2005'='X.47','2006'='X.48','2007'='X.49', '2008'='X.50','2009'='X.51','2010'='X.52', '2011'='X.53','2012'='X.54','2013'='X.55','2014'='X.56','2015'='X.57','2016'='X.58','2017'='X.59','2018'='X.60'))

Public.spending.on.health_New <- Public.spending.on.health_New[-1,]
```

Then, we use *pivot_longer* to attribute each value (Value_Spending.on.health) to the corresponding 'Time' and 'LOCATION'.

```{r}
Public.spending.on.health_New <- Public.spending.on.health_New %>% 
  pivot_longer(cols = c('2000','2001','2002','2003','2004','2005','2006','2007','2008','2009','2010','2011','2012','2013','2014','2015','2016','2017','2018'),names_to = 'Time', values_to = 'Value_Spending.on.health')
```

Finally we have a new dataframe of the Current health expenditure (% of GDP) of each countries attributed to the Time (from 2000 to 2018)

# 
Now we import the  share with mental and substance disorders data corresponding to a list of countries. Our goal is to compare the prevalence of mental health disorder in a population of a country with respect to the public investments on health.

```{r}
share.with.mental.and.substance.disorders <- read.csv2(here::here('data/Regression_3/share-with-mental-and-substance-disorders copie.csv'))
```

We rename the (share.with.mental.and.substance.disorders) dataframe into Mental_Health.

```{r}
Mental_Health <- share.with.mental.and.substance.disorders                                                       
```

We remove the 'Entity' column. Indeed we refer only to the LOCATION as code.
```{r}
Mental_Health <- Mental_Health[,-1]
```

We rename the variable column of year with Time, the Code with LOCATION and
Prevalence...Mental.and.substance.use.disorders...Sex..Both...Age..Age.standardized..Percent. with Mental_health_value.

```{r}
Mental_Health <- Mental_Health %>%
  rename(Time=Year)

Mental_Health <- Mental_Health %>%
  rename(LOCATION=Code)

Mental_Health1 <- rename(Mental_Health, 'Mental_health_Value' = 'Prevalence...Mental.and.substance.use.disorders...Sex..Both...Age..Age.standardized..Percent.')
```

After this, we want to filter the data with the value going from 2000 to 2017.

```{r}
Mental_Health <- Mental_Health1 %>%
  group_by(LOCATION,Mental_health_Value) %>%
  filter(Time>1999)
```

Our analysis is focus on a specific list of countries. We consider it relevant to take a sample of 28 countries with different structural characteristics.
Here is the following selected countries: 'AUT','BEL','HRV', 'CZE', 'DNK', 'ENG', 'FIN', 'FRA', 'DEU', 'GRC', 'HUN', 'ISL', 'ITA', 'ROU', 'PRT', 'POL', 'NOR', 'NLD', 'CHE', 'SWE', 'ESP', 'AUS', 'BRA', 'CAN', 'CHN', 'JPN', 'NZL', 'USA'

```{r}
List.of.Countries = c('AUT','BEL','HRV', 'CZE', 'DNK', 'ENG', 'FIN', 'FRA', 'DEU', 'GRC', 'HUN', 'ISL', 'ITA', 'ROU', 'PRT', 'POL', 'NOR', 'NLD', 'CHE', 'SWE', 'ESP', 'AUS', 'BRA', 'CAN', 'CHN', 'JPN', 'NZL', 'USA')

Mental_Health_2 <-  Mental_Health %>%
  filter(LOCATION %in% List.of.Countries)

Public.spending.on.health_New_2 <- Public.spending.on.health_New %>% 
  filter(LOCATION %in% List.of.Countries)
```

We merge the two dataframes into one single table named tab_1. We join them by LOCATION and Time.

```{r}
tab_1 <- merge(Public.spending.on.health_New_2, Mental_Health_2, by = c('LOCATION', 'Time'))
```

We need the values as numeric and not as characters for the analysis

```{r}
tab_1$Value_Spending.on.health <- as.numeric(tab_1$Value_Spending.on.health)
tab_1$Mental_health_Value <- as.numeric(tab_1$Mental_health_Value)
```




