---
title: "Data"
output: html_document
---


First, we need to install different packages. 
```{r, echo = FALSE, message = FALSE}
source(here::here("scripts/Setup.R"))
```

For our research, we are going to use different datasets for our three main themes. 



## Work Environment

First of all, for the database concerning the environment at work, we have extracted all the data from the sites : <https://www.oecd.org> and <https://ourworldindata.org>. 

Our first resarch question was : Given the structure of the working environment in different countries, can we say that the mental health of the population is influenced by the working conditions and the situation of the country?

To see those effects, we have chosen the information of 6 independants variables ; 

- the average work-time (Hours/worker)
- the GPD (US dollars/capita)
- the unemployment rate (% of labour force)
- the working age population (% of population)
- the average wages (US dollars)
- the income inequalities (Gini coefficient, 0=complete equality and 1=complete inequality)

 --> Regression 1 : MentalHealth = x1*IncomeInequality + x2*wages + x3*Unemployment + x4*WorkingAgePopulation + x5*WorkTime + x6*GPD

We have made a selection of several countries which are the following (To simplify, country codes have been used and not the full names) : Austria, Belgium, Croatia, Czechia, Denmark, Finland, France, Germany, Greece, Hungary, Iceland, Ireland, Italy, Romania, Portugal, Poland, Norway, Netherlands, Switzerland, Sweden, Spain, Australia, Brazil, Canada, Japan, New-Zealand and the USA.  

```{r}
List.of.Countries = c('AUT','BEL','HRV', 'CZE', 'DNK', 'ENG', 'FIN', 'FRA', 'DEU', 'GRC', 'HUN', 'ISL', 'ITA', 'ROU', 'PRT', 'POL', 'NOR', 'NLD', 'CHE', 'SWE', 'ESP', 'AUS', 'BRA', 'CAN', 'JPN', 'NZL', 'USA')
```

Now that we have collected all our data, we need to sort, order and rename them in order to obtain only tables with three columns to have the value of our variable according to its country and its date. We took the data for each of these variables for a certain sample of countries and then chose to do an individual average over the years from 2000 to 2017.

```{r}
Mental_Health <- read.csv(here::here("Data/Regression1/Mental_Health.csv"))
attach(Mental_Health)
Mental_Health <- Mental_Health[,-1]
Mental_Health <- rename(Mental_Health,c("LOCATION"="Code", "TIME"="Year","ValueH"="Prevalence...Mental.and.substance.use.disorders...Sex..Both...Age..Age.standardized..Percent."))
Mental_Health <-  Mental_Health %>% filter(LOCATION %in% List.of.Countries)
Mental_Health <- Mental_Health %>%
  filter(TIME>1999, TIME< 2018)
Mental_Health_m <- aggregate(Mental_Health[,3], list(Mental_Health$LOCATION), mean)
Mental_Health_m <- rename(Mental_Health_m,c("LOCATION"="Group.1","Mean_1"="x"))

Income_Inequality <- read.csv2(here::here("Data/Regression1/Income_inequality-1.csv"))
attach(Income_Inequality)
Income_Inequality <- Income_Inequality[,-c(2:5,8)]
Income_Inequality$Value <- as.numeric(Income_Inequality$Value)
Income_Inequality <-  Income_Inequality %>% filter(LOCATION %in% List.of.Countries)
Income_Inequality <- Income_Inequality %>%
  filter(TIME>1999, TIME< 2018)
Income_Inequality_m <- aggregate(Income_Inequality[,3], list(Income_Inequality$LOCATION), mean)
Income_Inequality_m <- rename(Income_Inequality_m,c("LOCATION"="Group.1","Mean_2"="x"))

wages <- read.csv(here::here("Data/Regression1/Average_wages.csv"))
attach(wages)
wages <- wages[,-c(2:5,8)]
wages <-  wages %>% filter(LOCATION %in% List.of.Countries)
wages <- wages %>%
  filter(TIME>1999, TIME< 2018)
wages_m <- aggregate(wages[,3], list(wages$LOCATION), mean)
wages_m <- rename(wages_m,c("LOCATION"="Group.1","Mean_3"="x"))

Unemployment <- read.csv(here::here("Data/Regression1/Unemployement_Rate.csv"))
attach(Unemployment)
Unemployment <- Unemployment[,-c(2:5,8)]
Unemployment <-  Unemployment %>% filter(LOCATION %in% List.of.Countries)
Unemployment <- Unemployment %>%
  filter(TIME>1999, TIME< 2018)
Unemployment_m <- aggregate(Unemployment[,3], list(Unemployment$LOCATION), mean)
Unemployment_m <- rename(Unemployment_m,c("LOCATION"="Group.1","Mean_4"="x"))

Working_Age <- read.csv(here::here("Data/Regression1/Working_age_population.csv"))
attach(Working_Age)
Working_Age <- Working_Age[,-c(2:5,8)]
Working_Age <-  Working_Age %>% filter(LOCATION %in% List.of.Countries)
Working_Age_m <- aggregate(Working_Age[,3], list(Working_Age$LOCATION), mean)
Working_Age_m <- rename(Working_Age_m,c("LOCATION"="Group.1","Mean_5"="x"))

Work_Time <- read.csv(here::here("Data/Regression_1/Avg Work_Time.csv"))
attach(Work_Time)
Work_Time <- Work_Time[,-c(2:5,8)]
Work_Time <-  Work_Time %>% filter(LOCATION %in% List.of.Countries)
Work_Time <- Work_Time %>%
  filter(TIME>1999, TIME< 2018)
Work_Time_m <- aggregate(Work_Time[,3], list(Work_Time$LOCATION), mean)
Work_Time_m <- rename(Work_Time_m,c("LOCATION"="Group.1","Mean_6"="x"))

GDP <- read.csv(here::here("Data/Regression1/gdp-per-capita.csv"))
attach(GDP)
GDP <- GDP[,-c(1,5)]
GDP <- rename(GDP,c("LOCATION"="Code", "TIME"="Year"))
GDP <-  GDP %>% filter(LOCATION %in% List.of.Countries)
GDP <- GDP %>%
  filter(TIME>1999, TIME< 2018)
GDP_m <- aggregate(GDP[,3], list(GDP$LOCATION), mean)
GDP_m <- rename(GDP_m,c("LOCATION"="Group.1","Mean_7"="x"))
```

Now that we have all our variables in the right format, we need to put them in a common table so that we can have an overall representation and be able to observe and analyze the trends that emerge.

```{r}
tab0 <- full_join(Mental_Health_m, Income_Inequality_m, by = c("LOCATION"))
tab1 <- full_join(tab0, wages_m, by = c("LOCATION"))
tab2 <- full_join(tab1, Unemployment_m, by = c("LOCATION"))
tab3 <- full_join(tab2, Working_Age_m, by = c("LOCATION"))
tab4 <- full_join(tab3, Work_Time_m, by = c("LOCATION"))
tab_R1 <- full_join(tab4, GDP_m, by = c("LOCATION"))
```
At this stage, we realized that for some of the countries we had selected (England, Hungary, Japan, Romania, Belgium, Brazil) the data was too insufficient to extract anything. And in order not to bias our results we chose to remove them from our analysis by using the "na.omit" function.

````{r}
tab_R1 <- na.omit(tab_R1)
tab_R1 <- rename(tab_R1, c("Mental_Health"="Mean_1","Income_Inequality"="Mean_2","wages"="Mean_3","Unemployment"="Mean_4","Working_Age"="Mean_5","Work_Time"="Mean_6","GDP"="Mean_7"))
```
This table allowed us to extract a plot and to start answering our questions. Unfortunately we could not see any real trend between our variables. So we decided to transform our data with the log function in order to reduce the range of our distribution. 

````{r}
tab_R1_log <- log(tab_R1[,2:8])
tab_Tot <- cbind(tab_R1$LOCATION, tab_R1_log)
tab_Tot <- rename(tab_Tot, c("LOCATION"="tab_R1$LOCATION"))

plot(tab_Tot)
```
This plot allows us to see how the variables we implemented affect mental health in these different countries. In spite of the use of the log function which improved our curves a little, the significance of our results is still not obvious. We will do further analysis later on but, at first sight, it does not seem that the work environment has a flagrant impact on the mental health of the population.





## Covid

For our second theme around Covid, we want to analyze if Covid had an impact on antidepressant 
consumption in selected countries around the world. We found data on antidepressant consumption on the website : <https://www.oecd.org>, in the Pharmaceutical Market Section. 
Regarding the Covid data, they come from the site : <https://coronavirus.jhu.edu>. 

Regression 2.1 : Antidepressant_consumption = a*Number_Covid-19_cases + b*Number_Covid-19_Death

Once again, we have made a selection of several countries which are the following : Austria, Belgium, Croatia, Czechia, Denmark, Finland, France, Germany, Greece, Hungary, Iceland, Ireland, Italy, Romania, Portugal, Poland, Norway, Netherlands, Switzerland, Sweden, Spain, Australia, Brazil, Canada, China, Japan, New-Zealand and the USA. 
Countries were selected based on available data, and this list includes the countries where there was the most data for our research.  

```{r, echo = FALSE, message = FALSE}
List.of.Countries = c('AUT','BEL','HRV', 'CZE', 'DNK', 'ENG', 'FIN', 'FRA', 'DEU', 'GRC', 'HUN','ISL',
                      'ITA', 'ROU', 'PRT', 'POL', 'NOR', 'NLD', 'CHE', 'SWE', 'ESP', 'AUS', 'BRA',
                      'CAN', 'CHN', 'JPN', 'NZL', 'USA')
```

For this first analysis related to the impact of Covid, R2.1, we quickly realized that the data available for antidepressant consumption in 2020 was very limited. We had to make a second selection of countries for this regression in order to observe only the countries with data in 2020, during the covid year. 

```{r, echo = FALSE, message = FALSE}
List.of.Countries2 = c('GRC', 'HUN', 'ISL', 'ITA', 'NOR','PRT', 'SWE', 'ESP')
```

Now we can select and sort the data. 
```{r, echo = FALSE, message = FALSE}
Antidepressant_consumption <- read.csv(here::here("Data/Regression2/Conso_Antidepressant.csv"))
attach(Antidepressant_consumption)
```

For all the variables we only kept the columns on the country, the date and the value of the variable, because they were the only ones that interested us. All the others have therefore been deleted.
It was also often necessary to rename the columns so that they all follow the scheme: LOCATION, TIME and VALUE. 

```{r, echo = FALSE, message = FALSE}
Antidepressant_consumption <- Antidepressant_consumption[,-c(1:4,6:7,10:11)]
Antidepressant_consumption <- rename(Antidepressant_consumption,c("LOCATION"="COU","TIME"="Year","Consumption"="Value"))
Antidepressant_consumption <- Antidepressant_consumption %>% filter(LOCATION %in% List.of.Countries)
Antidepressant_consumption1 <- Antidepressant_consumption %>% filter(LOCATION %in% List.of.Countries2)
```

We had to add a column with the date 2020 for the covid data, because it was not present. 
```{r, echo = FALSE, message = FALSE}
Number_Covid19_cases_deaths <- read.csv2(here::here("Data/Regression2/Cases + Deaths_Covid.csv"))
attach(Number_Covid19_cases_deaths)
Number_Covid19_cases_deaths <- Number_Covid19_cases_deaths[,-c(1,2,4:7,9:12)]
Number_Covid19_cases_deaths <- Number_Covid19_cases_deaths[-1,] 
Number_Covid19_cases_deaths <- rename(Number_Covid19_cases_deaths, "LOCATION"="Code")
Number_Covid19_cases_deaths <- Number_Covid19_cases_deaths %>% add_column(TIME = 2020, .after = "LOCATION") 
Number_Covid19_cases_deaths <-  Number_Covid19_cases_deaths %>% filter(LOCATION %in% List.of.Countries)
Number_Covid19_cases_deaths1 <-  Number_Covid19_cases_deaths %>% filter(LOCATION %in% List.of.Countries2)
```

We can now form a table with all the data together, using the *full_join* function. 

```{r, echo = FALSE, message = FALSE}
tab_R2.1 <- full_join(Number_Covid19_cases_deaths1, Antidepressant_consumption1, by= c("LOCATION","TIME"))
```

As the data of cases and death of the covid for the years before 2020 were displayed in NA, we assumed that its values were equal to 0. Also, the "cases" variable was output in character, we converted it to numeric.

```{r, echo = FALSE, message = FALSE}
tab_R2.1[is.na(tab_R2.1)] <- 0 
tab_R2.1$Cases...cumulative.total <- as.numeric(tab_R2.1$Cases...cumulative.total)
```
Our table on the use of antidepressants and the number of cases and deaths of covid is now ready to be used. 

Given the little information we had on antidepressant consumption in 2020 (only for 8 countries) we decided to observe the rate of depression and finally include it in our research question.
We therefore wanted to analyze the evolution of the depression rate between 2010 and 2017, and if the covid had an impact on it in 2021. Our data comes from the sites : <https://ourworldindata.org/mental-health#depression> and <https://worldpopulationreview.com/>. 

```{r, echo = FALSE, message = FALSE}
Depression_Rate2000_2017 <- read.csv(here::here("Data/Regression2/Depression_Rate_2000:2017.csv"))
attach(Depression_Rate2000_2017)
```

Here too we have only kept the country, the year and the value, and renamed the columns.As the years start before 2000, we have to make a selection of the years after 1999, to keep only what interests us. 

```{r, echo = FALSE, message = FALSE}
Depression_Rate2000_2017 <- Depression_Rate2000_2017[-1]
Depression_Rate2000_2017 <- rename(Depression_Rate2000_2017,c("LOCATION"="Code","TIME"="Year","Rate"="Prevalence...Depressive.disorders...Sex..Both...Age..Age.standardized..Percent."))
Depression_Rate2000_2017 <- Depression_Rate2000_2017 %>% filter(LOCATION %in% List.of.Countries)
Depression_Rate2000_2017 <- Depression_Rate2000_2017 %>%
  filter(TIME>1999)
Depression_Rate2017 <- Depression_Rate2000_2017 %>%
  filter(TIME>2016)
Depression_Rate2017 <- rename(Depression_Rate2017,c("2017"="Rate"))
Depression_Rate2017 <- Depression_Rate2017[-2]
```

We did exactly the same thing for the depression rate in 2021. 
```{r, echo = FALSE, message = FALSE}
Depression_Rate2021 <- read.csv2(here::here("Data/Regression2/Depression_Rate_2021.csv"))
attach(Depression_Rate2021)
Depression_Rate2021 <- Depression_Rate2021[,-c(1,3:4)]
Depression_Rate2021 <- rename(Depression_Rate2021,c("2021"="prevalence"))
Depression_Rate2021 <- Depression_Rate2021 %>% filter(LOCATION %in% List.of.Countries)
Depression_Rate2021 <- Depression_Rate2021 %>% add_column(TIME = 2021, .after = "LOCATION") 
Depression_Rate2021 <- Depression_Rate2021[-3]
```

Then, we had to join the two tables into one, using both *inner_join* and *pivot_longer* in order to obtain a table that we could use correctly afterwards to do analyses. 

```{r, echo = FALSE, message = FALSE}
Depression2017_2021 <- Depression_Rate2017 %>%
  inner_join(Depression_Rate2021, by = "LOCATION")
Depression2017_2021$"2021" <- as.numeric(Depression2017_2021$"2021")
Depression2017_2021 <- Depression2017_2021 %>%
  pivot_longer(c(`2017`, `2021`),
               names_to = "TIME",
               values_to = "Rate")
```

For the second study of this theme, we want to see whether teleworking and unemployment rates can affect antidepressant use in selected countries. Information on Teleworking and Unemployment rate were extracted respectively from the sites : <https://ec.europa.eu/eurostat> and <https://data.oecd.org>. 

We will now use the data of antidepressant according to the first selected country list. 

As above, we have kept only the columns we were interested in, i.e. value, date and country, and we have renamed some inadequate columns. 

```{r, echo = FALSE, message = FALSE}
Teleworking <- read.csv2(here::here("Data/Regression2/Teleworking.csv"))
attach(Teleworking)
Teleworking <- Teleworking[,-c(1:8,12)]
Teleworking <- rename(Teleworking,c("LOCATION"="geo","TIME"="TIME_PERIOD","Teleworking"="OBS_VALUE"))
Teleworking <-  Teleworking %>% filter(LOCATION %in% List.of.Countries)
```

We also did this for the unemployment rate. 

```{r, echo = FALSE, message = FALSE}
UnemploymentCovid <- read.csv(here::here("Data/Regression2/Unemployement_Rate.csv"))
attach(UnemploymentCovid)
UnemploymentCovid <- UnemploymentCovid[,-c(2:5,8)]
UnemploymentCovid <- rename(UnemploymentCovid, c("Unemployment"="Value"))
UnemploymentCovid <-  UnemploymentCovid %>% filter(LOCATION %in% List.of.Countries)
```

With the *full_join* function we have gathered the data of these three variables in a single table.
For the good functioning of the table for further analysis, it was necessary to remove the NA values, and to convert the variable "teleworking" in numerical (which was in character). 

```{r, echo = FALSE, message = FALSE}
tab <- full_join(Antidepressant_consumption, Teleworking, by=c("LOCATION", "TIME"))
tab_R2.2 <- full_join(tab, UnemploymentCovid, by = c("LOCATION", "TIME"))
tab_R2.2 <- na.omit(tab_R2.2)
tab_R2.2$Teleworking <- as.numeric(tab_R2.2$Teleworking)
```





### Public spendings on health 


In this thrid analysis of datasets,  we are going to compare the prevalence of mental health disorder (% of the population (age-standardaized)) in a population of a country and the current health expenditure (% of GDP). Particularly focus on the countries of the OCDE that is The Organisation for Economic Co-operation and Development.

The sources of our datas comes from the website : <https://data.worldbank.org/indicator/SH.XPD.CHEX.GD.ZS> for the current health expenditure in the countries and <https://ourworldindata.org/mental-health> for the Mental health datas.

Our intitial question of research is: 

- Can health care systems such as financial investments in overall health, access to medication explain and predict cross-country differences in mental disorders in the population? Is a country that invests more in public health for its population the country where there is less mental illness?

- Our influenced variable Y is therefore the prevalence of mental health disorder (% of the population)
- our independant variable X is the current health expenditure (% of the GDP)
- The access to medication is a difficulte variable to quantify, we did not find data corresponding to that. Therefore, our analysis is focus on these two variables X and Y. 


Importation of the dataset Public.spending on health. This dataframe represent Current health expenditure (% of GDP) of each countries.

```{r, echo = FALSE, message = FALSE}
Public.spending.on.health_New <- read.csv2(here::here('Data/Regression3/Public.spending.on.health.csv'))
```
                                       
This dataet of Public sprending on health has a bad structure initialy.
We remove the 3 first rows and we rename the different variables in the columns to get the same structure as previously.

```{r,echo = FALSE, message = FALSE}
Public.spending.on.health_New <- Public.spending.on.health_New[-c(1:3),]

Public.spending.on.health_New <- rename(Public.spending.on.health_New, c('Country' = 'Data.Source', 'LOCATION' = 'World.Development.Indicators'))
```

Then we need to remove the unecessary columns, with no data corresponding, which means the missing values from 1960 to 1999 and from 2019-2020. Deleting this columns will not biais our analysis because there are NA for every observations. We believe that the data about the public health expenditures started to be recorded in 2000.

Also, the **Indicator Name**, **Indicator Code** are unrelevant datas.

```{r,echo = FALSE, message = FALSE}
Public.spending.on.health_New <- Public.spending.on.health_New[,-c(5:44)]
Public.spending.on.health_New$X.61 <- NULL
Public.spending.on.health_New$Country <- NULL
Public.spending.on.health_New$X <- NULL
Public.spending.on.health_New$X.1 <- NULL
Public.spending.on.health_New$X.62 <- NULL
Public.spending.on.health_New$X.63 <- NULL
```

 Our initial dataframe as for variables names [(X.n),(X.n+1)...(X.m)], we need to transform them as Years (2000,2001...2018). 

```{r,echo = FALSE, message = FALSE}
Public.spending.on.health_New <- rename(Public.spending.on.health_New, c('2000'='X.42','2001'='X.43','2002'='X.44','2003'='X.45', '2004'='X.46','2005'='X.47','2006'='X.48','2007'='X.49', '2008'='X.50','2009'='X.51','2010'='X.52', '2011'='X.53','2012'='X.54','2013'='X.55','2014'='X.56','2015'='X.57','2016'='X.58','2017'='X.59','2018'='X.60'))

Public.spending.on.health_New <- Public.spending.on.health_New[-1,]
```

Then, we use **pivot_longer** to attribute each value (Value_Spending.on.health) to the corresponding 'Time' (the year) and 'LOCATION'(the code of the country). This will transform our dataframe with the years in rows and not in columns.

```{r,echo = FALSE, message = FALSE}
Public.spending.on.health_New <- Public.spending.on.health_New %>% 
  pivot_longer(cols = c('2000','2001','2002','2003','2004','2005','2006','2007','2008','2009','2010','2011','2012','2013','2014','2015','2016','2017','2018'),names_to = 'Time', values_to = 'Value_Spending.on.health')
```

Finally we have a new dataframe of the Current health expenditure (% of GDP) of each countries attributed to the Time (from 2000 to 2018).


# Now we import the  share with mental and substance disorders data corresponding to a list of countries. Our goal is to compare the prevalence of mental health disorder in a population of a country with respect to the public investments on health.

```{r,echo = FALSE, message = FALSE}
share.with.mental.and.substance.disorders <- read.csv2(here::here('Data/Régression 3/share-with-mental-and-substance-disorders copie.csv'))
```
This dataset has already a good structure, the same as the others for our analysis. The value Y; *prevalence mental and substance use disorders.sex.both.age stanrdaized percent*, represents more clearly the proportion of the population in % sufuring from mental illness in a given country. 

We rename our (share.with.mental.and.substance.disorders) dataframe into Mental_Health.

```{r,echo = FALSE, message = FALSE}
Mental_Health <- share.with.mental.and.substance.disorders                                                       
```

We remove the *Entity* column. Indeed we refer only to the LOCATION as code.
```{r,echo = FALSE, message = FALSE}
Mental_Health <- Mental_Health[,-1]
```

We rename the variable column of *year* with Time, the *Code* with LOCATION and
*Prevalence...Mental.and.substance.use.disorders...Sex..Both...Age..Age.standardized..Percent.* with Mental_health_value.

```{r,echo = FALSE, message = FALSE}
Mental_Health <- Mental_Health %>%
  rename(Time=Year)

Mental_Health <- Mental_Health %>%
  rename(LOCATION=Code)

Mental_Health1 <- rename(Mental_Health, 'Mental_health_Value' = 'Prevalence...Mental.and.substance.use.disorders...Sex..Both...Age..Age.standardized..Percent.')
```

After this, we want to filter the data with the value going from 2000 to 2017. Why do we keep only these values?
Because we consider it as a relevant horizon of time and we will need to fit these values to the public spendinds on health for our final table. So we must keep the same strucure.

```{r,echo = FALSE, message = FALSE}
Mental_Health <- Mental_Health1 %>%
  group_by(LOCATION,Mental_health_Value) %>%
  filter(Time>1999)
```

Our analysis is focus on a specific list of countries. We consider it relevant to take a sample of 28 countries with different structural characteristics. 
Here is the following selected countries: 'AUT','BEL','HRV', 'CZE', 'DNK', 'ENG', 'FIN', 'FRA', 'DEU', 'GRC', 'HUN', 'ISL', 'ITA', 'ROU', 'PRT', 'POL', 'NOR', 'NLD', 'CHE', 'SWE', 'ESP', 'AUS', 'BRA', 'CAN', 'CHN', 'JPN', 'NZL', 'USA'

The countries in this list our part of the OCDE. We make this selection because taking all the countries is the world would result to:
- Too many observations 
- Extreme values
- Unrelevant study 

```{r,echo = FALSE, message = FALSE}
List.of.Countries = c('AUT','BEL','HRV', 'CZE', 'DNK', 'ENG', 'FIN', 'FRA', 'DEU', 'GRC', 'HUN', 'ISL', 'ITA', 'ROU', 'PRT', 'POL', 'NOR', 'NLD', 'CHE', 'SWE', 'ESP', 'AUS', 'BRA', 'CAN', 'CHN', 'JPN', 'NZL', 'USA')

Mental_Health_2 <-  Mental_Health %>%
  filter(LOCATION %in% List.of.Countries)

Public.spending.on.health_New_2 <- Public.spending.on.health_New %>% 
  filter(LOCATION %in% List.of.Countries)
```

We merge the two dataframes into one single table named tab_1. We join them by LOCATION and Time. 

```{r,echo = FALSE, message = FALSE}
tab_1 <- merge(Public.spending.on.health_New_2, Mental_Health_2, by = c('LOCATION', 'Time'))
```

We need the values as numeric and not as characters for the analysis

```{r,echo = FALSE, message = FALSE}
tab_1$Value_Spending.on.health <- as.numeric(tab_1$Value_Spending.on.health)
tab_1$Mental_health_Value <- as.numeric(tab_1$Mental_health_Value)
```
```{r}
kable(tab_1)
```


