---
title: "Eda"
output: html_document
---


```{r, echo = FALSE, message = FALSE}
source(here::here("scripts/Setup.R"))
```


Now all our databases are clean and ready to be used. 

# 2 / Exploratory data analysis

### Map representing the mental illness prevalence in the selected countries from the OCDE

```{r}
mental.health <- share.with.mental.and.substance.disorders

mental.health <- mental.health %>%
  filter(Entity %in% tab.of.countries$Entity )

mental.health <- rename(mental.health, 'mental_health_Value' = 'Prevalence...Mental.and.substance.use.disorders...Sex..Both...Age..Age.standardized..Percent.')

mental.health$mental_health_Value <- as.numeric(mental.health$mental_health_Value)

mental.health <- mental.health[-2]

mental.health.new <- mental.health %>%
  group_by(Entity,mental_health_Value) %>%
  filter(Year>1999)
mapdata <- map_data('world')
mapdata <- rename(mapdata,'Entity'='region')

mapdata2 <- left_join(mapdata, mental.health , by='Entity')

map.1 <- ggplot(mapdata2, aes(x=long, y=lat, group=group, labels=Entity))+
  geom_polygon(aes(fill=mental_health_Value))+
  scale_fill_gradient(low = '#56B1F7', high = '#132B43')
```

```{r, fig.align="center"}
ggplotly(map.1)
```
----

## Mental health through the work environment

We will begin this analysis with a descending ranking of countries with the highest proportion of their population with mental health disorders. This will allow us to explain certain differences or similarities. 

```{r}
ggplot(data = tab_mean, aes(x = MentalHealth_mean, y=reorder(LOCATION,MentalHealth_mean))) + 
  geom_bar(stat='identity',fill="#DB7093",color="#DB7093",alpha=0.8) +
  geom_text(aes(label=round(MentalHealth_mean)),hjust=1,color='#4F2F4F') +
  xlab("Mental Health mean 2000-2017")+ ylab("Country")+
  ggtitle("Representation of the rate of mental health disorder by country and region")
```

On this first table, we can see that the Oceanian countries (Australia, New Zealand) are the ones that have a bigger part of their population with a mental disorder, followed by North America (Canada, USA) and Western Europe (France, Norway, Netherlands, Spain, Germany, Portugal). While Eastern European (Poland, Romania, Hungary, Czech Republic, Croatia) and Asian (Japan) countries have the lowest rate.  


```{r}
Graph_MH <- tab %>% ggplot(aes(
  x = TIME,
  y = Mental_Health,
  group = Entity,
  color = LOCATION
)) +
  geom_path() +
  theme(axis.text.x = element_text(
    angle = 360,
    hjust = 1,
    vjust = 0.5
  )) +
  ylim(0,20)+
  ggtitle("Evolution of mental health disorder over time and by country") +
  xlab("Time") + ylab("Prevalence of mental health value in %") 
ggplotly(Graph_MH)
```

This table shows that the prevalence of mental illness has hardly changed during the selected period from 2000 to 2017 for all countries in our database. Thus, we can conclude that time has no significant impact on the share of the population suffering from mental illness.

We now want to start studying our regression, that is, to see how the work environment, through the variables that compose it, impacts the percentage of mental health disorder in a country. For this we will do correlation analyses.


### Correlation analyses between mental health and the work environment

```{r, echo = FALSE, message = FALSE, eval=TRUE}
plot_tab <- plot(tab[3:9]) 
```
This plot does not allow us to make any conclusions about the implication of our variables on mental health. Indeed, we do not see any particular increase or decrease. Nevertheless, we can see a certain tendency translated by a linearity of the points which are not scattered in space either.
We will use a correlation matrix to put numbers on our hypotheses. 

### Corrplot

By using a correlation matrix, we will be able to put numbers on these connections.

```{r, echo = FALSE, message = FALSE, eval=TRUE}
Correlation <- cor(tab[3:9], use="pairwise.complete.obs")
corrplot_tab <- corrplot(Correlation, type = 'upper', method = 'number')
```

This confirms the assumptions formed by our first graphs, the positive coefficients indicating an increase in mental health and a contrario for the negative coefficient. 

In this corrplot, we can identify separently each correlation between our dependent variable Mental Health and the working environment independent ones.

Positive correlation observed:
- The highest correlation determined is the GDP; 0.51. It means if we increase by one unity the GDP (US dollars/capital) the prevalence of mental health is increase by 0.51.

- Mental health - Wages : a correlation of 0.48 shows a slightly increase. It is quite similar as the GDP impact. We can also doubt about a multicolinearity between GDP and wages (correlation of 0.76). That is why, we will check a little after the VIF. 

- Mental health - Income inequality : a correlation of 0.22 shows a slightly increase 

The variables left have a negative impact on the Mental health prevalence.

- Working age demonstrates a decrease of -0.34: As a reminder the working age population is the percentage of the population that is able to work in %, (15-65 years). It means if the working age proportion increases by 1%, the mental health value decreases by -0.34%.

- Same effect for the Work-time. The more a worker workers on average, the less a population suffers from mental illness. 

- Surprisingly, the Unemployment rate has no correlation with mental health. The slope coefficient is -0.06, close to zero.

Finally, In the correlation matrix we could see that some of our explanatory variables were particularly correlated. We will therefore check that there is not too much multicollinearity which could bias our results.

```{r}
vif(mod) 
```
We can see that none of these value is higer than 5 so we can conclude that our model is ready to be analysed more precisly.

We will also check the validity of our model by doing a regression.

### Regression study

$$Analysis 1 : MentalHealth = a*IncomeInequality + b*wages + c*Unemployment + d*WorkingAgePopulation + e*WorkTime + f*GPD + ε$$

```{r}
mod <- lm(Mental_Health ~ Income_Inequality + Wages + Unemployment + Working_Age + Work_Time + GDP + TIME, data = tab)
tab_model(mod,p.style = "stars",show.ci = FALSE, string.pred = "Coeffcient")
```

On this model, we can see that our model is approximately 80% explained by the variables we have chosen. Moreover, we notice that our variables, income inequality, wages, unemployment, working age and GDP are very significant. In fact, two variables show a real impact on mental health, they are income inequality and working age. Indeed, their coefficients of 25.42 and -0.41 are significantly high while that of our other variables is closer to 0. 
On the other hand, the time an employee spends working does not seem to have an impact on the rate of mental health disorder. We will therefore not take it into account as an explanatory variable for our problem. 
Another variable that is checked here is 'Time'. We see in the regression that it is significant and that its coefficient is close to 0, which confirms our first plot. Indeed, the proportion of population with a mental disorder can be calculated every year but it is rather constant through the years. 

We can conclude that our model is rather reliable and that the working environment considered has a moderate to low impact on the mental health of workers in the OECD countries.  

We will now see more precisely how each of these variables impact these diseases, always according to the countries through 2000 and 2017.

### Impact of work environment's variables on mental health disorders by country

Using these graphs and our two first tables, we can make these important points about the impact of the work environment on mental health in a population:

##### Income Inequality Analysis 
```{r, warning=FALSE}
ggplot(data = tab, mapping = aes(x = tab$Income_Inequality, y = tab$Mental_Health)) +
  geom_point(mapping = aes(color = LOCATION)) +
  geom_smooth() +
  xlim(0,0.5) + 
  ylim(0,20)+
  xlab("Income inequality (Gini coef.") + ylab("Prevalence of mental health (in %)") 
```

The higher the income inequality in a country, the more likely that country will have a high proportion of its population with mental disorders. (-)


##### Average wages Analysis
```{r, warning=FALSE}
ggplot(data = tab, mapping = aes(x = tab$Wages, y = tab$Mental_Health)) +
  geom_point(mapping = aes(color = LOCATION)) +
  geom_smooth()+
  xlim(0,70000) + 
  ylim(0,20)+
  xlab("Average wages (US$") + ylab("Prevalence of mental health (in %)") 
```

The higher the average wage in a country, the more likely that country will have a high proportion of its population with mental disorders. (-)


##### Unemployment rate Analysis
```{r, warning=FALSE}
ggplot(data = tab, mapping = aes(x = tab$Unemployment, y = tab$Mental_Health)) +
  geom_point(mapping = aes(color = LOCATION)) +
  geom_smooth() +
  xlim(0,28.0) + 
  ylim(0,20)+
  xlab("Unemployment rate (in %)") + ylab("Prevalence of mental health (in %)") 
```

The higher the unemployment rate in a country, the more likely that country will have a high proportion of its population with mental disorders. (-)


##### Working age of a population Analysis
```{r, warning=FALSE}
ggplot(data = tab, mapping = aes(x = tab$Working_Age, y = tab$Mental_Health)) +
  geom_point(mapping = aes(color = LOCATION)) +
  geom_smooth() +
  ylim(0,20)+
  xlab("Working age population (in %)") + ylab("Prevalence of mental health (in %)") 
```
--> Decrire l'axe qui commence a 60% 
The higher the percentage of a country's working-age population, the lower the proportion of its population with mental disorders. (+)


##### GDP Analysis
```{r, warning=FALSE}
ggplot(data = tab, mapping = aes(x = tab$GDP, y = tab$Mental_Health)) +
  geom_point(mapping = aes(color = LOCATION)) +
  geom_smooth() +
  xlim(0,84057) + 
  ylim(0,20)+
  xlab("GDP (US dollars/capita)") + ylab("Prevalence of mental health (in %)") 
```

The higher the GDP of a country, the more likely that country will have a high proportion of its population with mental disorders. (-)


In summary, a country with a medium wage, high GDP does not promote good mental health of workers. Second, high unemployment and income inequality worsen the mental health of a population. Nevertheless, if a country has a high proportion of working age population, it will have less problems related to the mental health of its workers.

----



## Impact of Covid-19



Firstly, we would like to know if there is a correlation between Cases or Deaths of Covid and the Value of Antidepressant Consumption through the years. We want to observe whether there is a peak in the consumption of these medications because of the covid crisis. Indeed, we make the hypothesis that due to this crisis, the proportion of people suffering from depression has increased, which would have had a significant impact on this consumption in 2020. 


```{r}
graph.antidepressant.consumption <- ggplot(data = Antidepressant_consumption) +
  geom_point(mapping = aes(x = TIME, y = Antidepressant_Consumption, color = LOCATION))+
  geom_line(mapping = aes(x = TIME, y = Antidepressant_Consumption, color = LOCATION))+
  annotate("rect", xmin = 2019, xmax = 2021, ymin = -1, ymax = max(Antidepressant_consumption$Antidepressant_Consumption),
           alpha = .2, fill = "orange")+
  xlab("Time")+ ylab("Antidepressant consumption")+
  ggtitle("Evolution of antidepressant consumption by country from 2000 to 2020")
ggplotly(graph.antidepressant.consumption)
```
By creating a graph of antidepressant consumption over time, we can see that, for our first selection of countries, antidepressant consumption is increasing over the years. We will see, in the analysis, if Covid Cases or Deaths are correlated to this increase.  




Due to lack of data on antidepressant use in 2020, it would be interesting to observe the rate of depression by country between 2000 and 2021. Here is the graph of depression rate by selected countries between 2000 and 2021. It is important to notice that we could not find the data for the years 2018, 2019 and 2020. So we have no data available for these years. 

```{r}
graph.depression.rate <- ggplot(data = Depression_Rate2000_2021)+
  geom_point(mapping = aes(x = TIME , y = Depression_Rate, color = LOCATION))+
  geom_line(mapping = aes(x = TIME , y = Depression_Rate, color = LOCATION))+
  annotate("rect", xmin = 2019, xmax = 2021, ymin = 0, ymax = max(Depression_Rate2000_2021$Depression_Rate),
           alpha = .2, fill = "orange")+
  xlab("Time")+ ylab("Depression Rate")+
  ggtitle("Evolution of the depression rate by country from 2000 to 2020")
 ggplotly(graph.depression.rate)          
```

```{r}

Depression_Rate2000_2021 <- Depression_Rate2000_2017 %>%
  rbind(Depression_Rate2021)%>%
  arrange(LOCATION,TIME)

Depression_Rate2000_2021 <- ddply(Depression_Rate2000_2021, .(LOCATION),
                                  function (d) {
                                    d$Growth <- c(NA, tail(d$Depression_Rate, -1) - head(d$Depression_Rate, -1))
                                    d
                                    }
                                  )
                                  
kbl(Depression_Rate2000_2021[1:38,],caption = "**Table of depression rate and its growth over the years**") %>%
  kable_classic(full_width = T, html_font = "Cambria") %>%
  kable_styling(bootstrap_options = c('striped', 'hover', 'condensed'))%>%
  add_footnote(
      paste(
         "Representation of the first 38 observation of the dataset. Total observations : ",
         nrow(Depression_Rate2000_2021)
      )
   )

```
Here we have calculated the growth each year until 2017, and between 2017 and 2021 of the depression rate by country. The table above shows only the first two countries in the list, Australia and Austria. 
We can indeed observe a growth over the years, but this increase is smaller and smaller or almost constant over time, when observing the above values for this two countries. We can therefore make the assumption that this growth continues to decline through the years after 2017. Following this trend, we can well notice that the value in 2021 is unusual compared to previous years. For example, Austria recorded a depression rate of 5.1% in 2021, an increase of 1.84% between 2017 and 2021.
There has been a strong increase in the depression rate in 2021, that we can well observe on the graph too. 






We will now focus on our second study, which is the evolution of antidepressant consumption as a function of teleworking and unemployment rate. 

```{r}
Reg2.2 <- lm(Antidepressant_Consumption~Teleworking+Unemployment+TIME, data = tab_R2.2)
tab_model(Reg2.2, p.style = "stars",show.ci = FALSE, string.pred = "Coeffcient")
```

With the *tab_model* function we can see a significant increase for one unit of  1.70310 * ValueAntidepressantConsumption for "Teleworking". This variable is significant with 2 stars wich is satisfying. However, "Unemployment" is not significant as it represents an increase for one unit of 0.16 * ValueAntidepressantConsumption, without any stars. For the "TIME" variable, the slope coefficient shows that there is indeed a increase in the antidepressant consumption every year by 1.61. However, it is not very significant and it can not really explain the variance of the model.
Moreover, R^2 is equal to 0,0867 which means that our model is explained by 8,7% of the variance, which is not very satisfying. This means that variables we don't know, have a more significant impact on antidepressant consumption in a country.

Given the results, and that the variable "unemployment" has not a significant impact on antidepressant consumption, we will remove this variable for the rest of our analysis. We will now now focus on teleworking and analyze the link between this variable and antidepressant consumption with different graphs.


```{r}
graph.teleworking <- ggplot(data = tab_R2.2) +
  geom_point(mapping = aes(x = TIME, y = Teleworking, color = LOCATION))+
  geom_line(mapping = aes(x = TIME, y = Teleworking, color = LOCATION))+
  annotate("rect", xmin = 2019, xmax = 2021, ymin = -1, ymax = 16, na.rm = T,
           alpha = .2, fill = "orange")+
  xlab("Time")+ ylab("Teleworking")+
  ggtitle("Evolution of teleworking by country from 2000 to 2020")
ggplotly(graph.teleworking)
```

It is important to note that all our analysis is done between the years 2000 and 2020, which is why the graph above starts in 2000. However, data we have on teleworking only starts in 2010. 

By making a graph of the evolution of teleworking per country, between 2010 and 2020, given the data available for this variable, we can see an increase of this rate in 2020. This increase can be explained by the Covid crisis. So, if we find a potential correlation between the consumption of antidepressants and teleworking, we could then make a link with the Covid. 


----

## How public spending on health impacts mental health in OECD countries

 In this primary analysis, we are going to determine the relationship between the *mental health disorder prevalence*, which is represented in percent, and the *Public spendings on health* that represent the current expenditures in public health of a country, in pourcent.
 
- Graphical observations and regression interpretation. 

```{r}
 plot(tab_1)
```
In this general plot, we can assume that *Time* is impacting the *value spending on health*. However, the impact on the *mental health value* seems close to zero. Furthermore, *Mental health* and *spendings on health* look positively correlated. 


- Creation of a corrplot in order to identify directly the correlation coefficient between the variables.

```{r}
corrplot(cor(tab_1[4:6]), method = 'number')
```
With this corrplot, we can identify the correlation values for each variable. The mental health value, as our dependent variable (Y) as for coefficient value 0.6 with the value spending on health. As predicted with the initial plot, Time does not impact mental health because the value is close to 0 and does not appear on the graph.

Graph.1 : Visualization of prevalence of mental health (% of the population) against Time for OCDE countries from 2000 to 2017 
```{r}
Graph_mental_health<- Mental_Health_2 %>% ggplot(aes(
  x = Time,
  y = Mental_health_Value,
  group = Entity,
  color = Region
)) +
  geom_path() +
  theme(axis.text.x = element_text(
    angle = 360,
    hjust = 1,
    vjust = 0.5
)) +
  ylim(0,20)+
  xlab("Time") + ylab("Prevalence of mental health value in %")+
  ggtitle("Evolution of the prevalence of mental health disorder in OCDE countries from 2000 to 2017")
  
ggplotly(Graph_mental_health)
```
Visually, the Time does not affect the value of our dependent variable and it appears that the distribution of values is based on the location.
We can see that the prevalence of mental health disorder does not rise through time. Indeed the variation appears small over time and the correlation negative.

- Statistical analysis of Mental health value evolution and the time:

```{r}
Regression.1.Time <- lm(Mental_health_Value ~ Time, data = tab_1)
```
```{r}
tab_model(Regression.1.Time, p.style = "stars",show.ci = FALSE, string.pred = "Coeffcient")
```
As visually analysed, the time does not impact our Y. The coefficient is not significant, the variance of the model is explained at 0.03% which is extremely low. The p-value is also high (0.7).
We conclude that this first model based only on ‘Time’ is bad. 

Graph.2 : Visualization of *Public spending on health* evolution between the OCDE countries from 2000 to 2018
```{r}
Graph_public.spending.on.health <- Public.spending.on.health_New_2 %>% ggplot(aes(
  x = Time,
  y = Value_Spending.on.health,
  group = Entity,
  color = Region
)) +
  geom_path() +
  theme(axis.text.x = element_text(
    angle = 360,
    hjust = 1,
    vjust = 0.5
)) +
  ylim(0,20)+
  xlab("Time") + ylab("Value spending on health in % of GDP")+
  ggtitle("Evolution of the public spending on health in OCDE countries from 2000 to 2018")
  

ggplotly(Graph_public.spending.on.health)
```
It appears that the distribution of values is based on *Location*, like *Mental health*. And also, the values according to each country seems to slightly increase through Time.


- Comparison of the 2 variables: 
Now we want to compare the two variables: x = Value_Spending.on.health., y = Mental_health_Value In order to see if the expenditure on health of a country from the OCDE impacts the prevalence of mental illness in its population.

Graph.3
```{r}
Graph.region <- ggplot(tab_1, aes(x=Value_Spending.on.health, y=Mental_health_Value, colour=Region, group=Entity, labels=Time)) + geom_point() + ylim(0,20)
ggplotly(Graph.region)
```

We observe that the two variables are positively correlated. However, it looks paradoxical, because the more a country invests on public health, the more there is the prevalence of mental illness. 

This result is not relevant and satisfactory for several reasons:
The first is that when comparing the mental health of a country with only health investment data, we omit variables in our model.

- Omitted variable bias: If we take the example of GDP, this variable influences not only health expenditure but also mental health problems as seen earlier with the first research question 'work environment'. 

- simultaneity bias: secondly, we are probably facing a simultaneity bias! Public spending on health cannot be considered as an exogenous variable. x also varies in reaction to y.

Therefore, we decide to observe the opposite. Is a country suffering from a big proportion of mental illness, a country that invests the most on public health?
We decide to reverse the research question for this analysis because it is more logical to put  x = Mental_health_Value , y = Value_Spending.on.health. We stay aware of this suniltaneity problem. 

Graph.4
```{r}
Graph.region2 <- ggplot(tab_1, aes( x = Mental_health_Value , y = Value_Spending.on.health, colour=Region, group=Entity)) +
  geom_point()+ ylim(0,20)
ggplotly(Graph.region2)
```
The fact that we allocate the colors to the region of the country is to shed the light on the distributions of the values according to the location in the world.
As a first result, the values are distributed in a similar way according to the region of the country.

----------------------
 
 
 
 
 
 
 
